---
title: "Recruitment and participant progress"
subtitle: "Operational monitoring dashboard"
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: monitoring-setup

library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(ggplot2)
library(scales)
library(knitr)
library(yaml)
library(htmltools)
library(patchwork)
source("operational_tracking_helpers.R")

config <- read_yaml("dashboard_config.yml")
id_column_type <- cols(uniqueid = col_character())
recruitment <- read_csv(
  config$files$recruitment, col_types = id_column_type, show_col_types = FALSE
)
enrolment <- read_csv(
  config$files$enrolment, col_types = id_column_type, show_col_types = FALSE
)
cimc <- read_csv(
  config$files$cimc, col_types = id_column_type, show_col_types = FALSE
)
refresh_metadata <- read_csv(config$files$refresh_metadata, show_col_types = FALSE)

data_mode <- tolower(config$data_source$mode)
mode_settings <- config$data_source[[data_mode]]
publish_action_lists <- isTRUE(mode_settings$publish_action_lists_in_rendered_site)
data_source_label <- if (data_mode == "production") "Kobo API production data" else "Linked dummy development data"
data_prepared_at <- first(refresh_metadata$prepared_at_utc)

site_labels <- unlist(config$labels$sites)
site_targets <- unlist(config$study$site_targets)
data_cutoff <- as.Date(first(refresh_metadata$effective_data_cutoff))
expected_study_days <- config$study$expected_daily_reports
missed_days_threshold <- config$monitoring$consecutive_missed_days
monthly_due_day <- config$study$monthly_due_day
followup_complete_label <- paste0("Reached day ", expected_study_days)

recruitment <- recruitment |>
  mutate(
    uniqueid = as.character(uniqueid),
    recruitment_date = as.Date(recruitment_date),
    planned_enrollment_date = as.Date(as.character(enrollment_date)),
    phone = as.character(phone),
    email = as.character(email),
    site = factor(unname(site_labels[organization]), levels = unname(site_labels))
  )

enrolment <- enrolment |>
  mutate(
    uniqueid = as.character(uniqueid),
    enrollment_date = as.Date(as.character(enrollment_date)),
    contraception_start_date = as.Date(as.character(contraception_start_date)),
    phone = as.character(phone),
    email = as.character(email),
    daily_reminder_method = as.character(daily_reminder_method),
    missed_days_reminder_method = as.character(missed_days_reminder_method),
    site = factor(unname(site_labels[organization]), levels = unname(site_labels))
  )

# Preserve every submitted record for protocol monitoring, but use one current
# record per participant for operational calculations. Kobo's numeric `_id`
# increases with each submission; the highest ID is treated as the current row.
canonical_latest_record <- function(data) {
  source_order <- seq_len(nrow(data))
  kobo_order <- if ("_id" %in% names(data)) {
    suppressWarnings(as.numeric(data[["_id"]]))
  } else {
    rep(NA_real_, nrow(data))
  }
  data |>
    mutate(.canonical_order = coalesce(kobo_order, as.numeric(source_order))) |>
    arrange(uniqueid, desc(.canonical_order)) |>
    distinct(uniqueid, .keep_all = TRUE) |>
    select(-.canonical_order)
}

recruitment_records <- recruitment
enrolment_records <- enrolment
recruitment <- canonical_latest_record(recruitment_records)
enrolment <- canonical_latest_record(enrolment_records)

cimc <- cimc |>
  mutate(
    uniqueid = as.character(uniqueid),
    date = as.Date(as.character(date)),
    method_stop_date = as.Date(as.character(QB))
  ) |>
  left_join(
    enrolment |>
      transmute(
        uniqueid, organization, site, enrollment_date,
        programme_start_date = contraception_start_date,
        enrolment_record_present = TRUE
      ),
    by = "uniqueid"
  )

# Automated protocol flags are screening signals for study-team adjudication.
# They deliberately use exact participant-ID matching so linkage problems are
# visible rather than silently corrected.
protocol_rules <- config$protocol_monitoring$rules
empty_protocol_review <- tibble(
  participant_id = character(), classification = character(), flag_code = character(),
  issue = character(), source_form = character(), record_date = as.Date(character()),
  site = character(), records = integer(), detail = character(),
  suggested_action = character(), review_status = character()
)

make_protocol_flags <- function(data, code, issue, source_form, detail, suggested_action) {
  rule <- protocol_rules[[code]]
  if (is.null(rule) || !isTRUE(rule$enabled) || nrow(data) == 0) {
    return(empty_protocol_review)
  }
  severity <- tolower(rule$severity)
  if (!severity %in% c("deviation", "violation")) {
    stop("Protocol rule ", code, " severity must be 'deviation' or 'violation'.")
  }
  data |>
    transmute(
      participant_id = as.character(uniqueid),
      classification = if_else(
        severity == "violation", "Potential violation", "Potential deviation"
      ),
      flag_code = code,
      issue = issue,
      source_form = source_form,
      record_date = as.Date(record_date),
      site = as.character(site),
      records = as.integer(records),
      detail = detail,
      suggested_action = suggested_action,
      review_status = "Needs review"
    )
}

protocol_review <- bind_rows(
  make_protocol_flags(
    cimc |>
      filter(is.na(enrolment_record_present)) |>
      distinct(uniqueid, date, .keep_all = TRUE) |>
      transmute(uniqueid, record_date = date, site, records = 1L),
    "cimc_without_enrolment",
    "CIMC submission has no matching enrollment record",
    "CIMC",
    "The participant ID was present in CIMC but absent from enrollment.",
    "Verify the ID and enrollment history; document and adjudicate the event."
  ),
  make_protocol_flags(
    enrolment |>
      filter(is.na(contraception_start_date)) |>
      transmute(uniqueid, record_date = enrollment_date, site, records = 1L),
    "missing_programme_start_date",
    "Enrollment has no valid programme start date",
    "Enrollment",
    "A programme start date is required to define follow-up and cycle timing.",
    "Verify the source record and correct it through the approved data process."
  ),
  make_protocol_flags(
    cimc |>
      filter(!is.na(enrollment_date), !is.na(date), date < enrollment_date) |>
      distinct(uniqueid, date, .keep_all = TRUE) |>
      transmute(uniqueid, record_date = date, site, records = 1L),
    "cimc_before_enrolment",
    "CIMC report is dated before enrollment",
    "CIMC",
    "The report date precedes the linked participant's enrollment date.",
    "Check form dates, time zone, participant ID, and whether follow-up began early."
  ),
  make_protocol_flags(
    cimc |>
      count(uniqueid, date, site, name = "records") |>
      filter(records > 1) |>
      transmute(uniqueid, record_date = date, site, records),
    "duplicate_cimc_participant_date",
    "More than one CIMC submission for a participant-day",
    "CIMC",
    "Multiple submissions share the same participant ID and report date.",
    "Determine whether this is a correction, duplicate, or additional submission."
  ),
  make_protocol_flags(
    enrolment_records |>
      count(uniqueid, name = "records") |>
      filter(records > 1) |>
      left_join(
        enrolment |>
          transmute(uniqueid, record_date = enrollment_date, site),
        by = "uniqueid"
      ) |>
      transmute(uniqueid, record_date, site, records),
    "duplicate_enrolment_participant",
    "More than one enrollment submission for a participant",
    "Enrollment",
    "Multiple enrollment records share the same participant ID.",
    "Verify whether the later record is an authorised correction and adjudicate the duplicate."
  ),
  make_protocol_flags(
    enrolment |>
      anti_join(recruitment |> distinct(uniqueid), by = "uniqueid") |>
      transmute(uniqueid, record_date = enrollment_date, site, records = 1L),
    "enrolment_without_recruitment",
    "Enrollment has no matching recruitment record",
    "Enrollment",
    "The participant ID was present in enrollment but absent from recruitment.",
    "Verify recruitment history and participant ID; adjudicate against the protocol."
  )
) |>
  arrange(factor(classification, c("Potential violation", "Potential deviation")),
          issue, participant_id, record_date)

protocol_summary <- protocol_review |>
  group_by(classification, issue) |>
  summarise(
    participants = n_distinct(participant_id),
    flagged_records = sum(records),
    .groups = "drop"
  ) |>
  arrange(factor(classification, c("Potential violation", "Potential deviation")),
          desc(participants), issue)

method_stops <- cimc |>
  filter(QA == 0, !is.na(method_stop_date)) |>
  group_by(uniqueid) |>
  summarise(method_stop_date = min(method_stop_date), .groups = "drop")

daily_counts <- cimc |>
  distinct(uniqueid, date) |>
  group_by(uniqueid) |>
  summarise(
    daily_reports_received = n(),
    first_report_date = min(date),
    last_report_date = max(date),
    .groups = "drop"
  )

monthly_counts <- cimc |>
  filter(monthly_report_due == "yes") |>
  distinct(uniqueid, date) |>
  count(uniqueid, name = "monthly_reports_received")

count_monthly_due_dates <- function(start_date, end_date) {
  if (is.na(start_date) || is.na(end_date) || end_date < start_date) return(0L)
  sum(as.integer(format(seq(start_date, end_date, by = "day"), "%d")) == monthly_due_day)
}

last_monthly_due_date <- function(start_date, end_date) {
  if (is.na(start_date) || is.na(end_date) || end_date < start_date) return(as.Date(NA))
  dates <- seq(start_date, end_date, by = "day")
  dates <- dates[as.integer(format(dates, "%d")) == monthly_due_day]
  if (length(dates) == 0) as.Date(NA) else max(dates)
}

progress <- enrolment |>
  left_join(method_stops, by = "uniqueid") |>
  left_join(daily_counts, by = "uniqueid") |>
  left_join(monthly_counts, by = "uniqueid") |>
  mutate(
    planned_end_date = enrollment_date + expected_study_days - 1L,
    observation_end_date = pmin(
      planned_end_date, data_cutoff, coalesce(method_stop_date, data_cutoff),
      na.rm = TRUE
    ),
    expected_daily_reports = pmax(0L, as.integer(observation_end_date - enrollment_date) + 1L),
    daily_reports_received = replace_na(daily_reports_received, 0L),
    monthly_reports_received = replace_na(monthly_reports_received, 0L),
    expected_monthly_reports = map2_int(
      enrollment_date, observation_end_date, count_monthly_due_dates
    ),
    last_monthly_report_due = as.Date(map2_dbl(
      enrollment_date, observation_end_date,
      ~ as.numeric(last_monthly_due_date(.x, .y))
    ), origin = "1970-01-01"),
    daily_completion = if_else(
      expected_daily_reports > 0,
      daily_reports_received / expected_daily_reports,
      NA_real_
    ),
    monthly_completion = if_else(
      expected_monthly_reports > 0,
      monthly_reports_received / expected_monthly_reports,
      NA_real_
    ),
    status = case_when(
      !is.na(method_stop_date) & method_stop_date <= data_cutoff ~ "Stopped method / follow-up ended",
      planned_end_date <= data_cutoff ~ followup_complete_label,
      daily_reports_received == 0 ~ "Enrolled — no daily report",
      TRUE ~ "Active follow-up"
    )
  )

current_missing_streak <- function(start_date, end_date, received_dates) {
  if (is.na(start_date) || is.na(end_date) || end_date < start_date) return(0L)
  due_dates <- seq(start_date, end_date, by = "day")
  missing <- !due_dates %in% received_dates
  streak <- rle(rev(missing))
  if (length(streak$values) == 0 || !streak$values[[1]]) 0L else streak$lengths[[1]]
}

received_dates_by_id <- split(cimc$date, cimc$uniqueid)
progress$current_consecutive_missed_days <- map2_int(
  progress$uniqueid,
  progress$observation_end_date,
  function(uid, end_date) {
    received <- received_dates_by_id[[uid]]
    if (is.null(received)) received <- as.Date(character())
    current_missing_streak(
      progress$enrollment_date[progress$uniqueid == uid], end_date, received
    )
  }
)

progress <- progress |>
  mutate(
    preferred_missed_reminder = case_when(
      !is.na(missed_days_reminder_method) ~ missed_days_reminder_method,
      str_detect(coalesce(daily_reminder_method, ""), "whatsapp") ~ "whatsapp",
      str_detect(coalesce(daily_reminder_method, ""), "text_message_sms") ~ "text_message_sms",
      str_detect(coalesce(daily_reminder_method, ""), "email") ~ "email",
      TRUE ~ daily_reminder_method
    ),
    reminder_contact = case_when(
      preferred_missed_reminder == "email" ~ email,
      preferred_missed_reminder %in% c("whatsapp", "text_message_sms") ~ phone,
      TRUE ~ coalesce(phone, email)
    )
  )

# Operational exports are regenerated whenever the dashboard is rendered.
reminder_targets <- progress |>
  filter(
    status == "Active follow-up",
    current_consecutive_missed_days >= missed_days_threshold
  ) |>
  transmute(
    participant_id = uniqueid, organization, site,
    current_consecutive_missed_days, last_report_date,
    reminder_method = preferred_missed_reminder, reminder_contact,
    daily_completion
  ) |>
  arrange(desc(current_consecutive_missed_days), site, participant_id)

eligible_not_enrolled <- recruitment |>
  filter(
    eligibility_status == "eligible",
    as.integer(data_cutoff - recruitment_date) >= config$monitoring$eligible_not_enrolled_after_days
  ) |>
  anti_join(enrolment, by = "uniqueid") |>
  transmute(
    participant_id = uniqueid, organization, site, recruitment_date,
    days_since_recruitment = as.integer(data_cutoff - recruitment_date),
    planned_enrollment_date, phone, email, reminder, notes
  ) |>
  arrange(desc(days_since_recruitment), site)

no_daily_targets <- progress |>
  filter(
    daily_reports_received == 0,
    as.integer(data_cutoff - enrollment_date) >= config$monitoring$no_daily_report_after_days,
    status != "Stopped method / follow-up ended"
  ) |>
  transmute(
    participant_id = uniqueid, organization, site, enrollment_date,
    days_since_enrollment = as.integer(data_cutoff - enrollment_date),
    daily_reminder_method, phone, email
  ) |>
  arrange(desc(days_since_enrollment), site)

monthly_due_targets <- progress |>
  filter(
    expected_monthly_reports > monthly_reports_received,
    !is.na(last_monthly_report_due),
    as.integer(data_cutoff - last_monthly_report_due) >= config$monitoring$monthly_report_grace_days
  ) |>
  transmute(
    participant_id = uniqueid, organization, site,
    expected_monthly_reports, monthly_reports_received,
    monthly_reports_missing = expected_monthly_reports - monthly_reports_received,
    last_monthly_report_due, reminder_method = preferred_missed_reminder,
    reminder_contact
  ) |>
  arrange(desc(monthly_reports_missing), site, participant_id)

write_csv(reminder_targets, "reminder_targets_3_consecutive_missed_days.csv", na = "")
write_csv(eligible_not_enrolled, "eligible_not_enrolled_targets.csv", na = "")
write_csv(no_daily_targets, "enrolled_no_daily_submission_targets.csv", na = "")
write_csv(monthly_due_targets, "monthly_report_due_targets.csv", na = "")
write_csv(protocol_review, "protocol_deviation_violation_review.csv", na = "")
progress_export <- progress |>
  transmute(
    participant_id = uniqueid, organization, site, enrollment_date,
    planned_end_date, status, daily_reports_received, expected_daily_reports,
    daily_completion, monthly_reports_received, expected_monthly_reports,
    monthly_completion, current_consecutive_missed_days, last_report_date,
    method_stop_date
  )
write_csv(progress_export, "participant_progress_summary.csv", na = "")

write_site_versions <- function(data, filename, organization_field = "organization") {
  for (site_code in names(site_labels)) {
    site_name <- unname(site_labels[[site_code]])
    if (organization_field %in% names(data)) {
      site_data <- data |> filter(.data[[organization_field]] == site_code)
    } else {
      site_data <- data |> filter(as.character(site) == site_name)
    }
    site_filename <- str_replace(filename, "\\.csv$", paste0("_", site_code, ".csv"))
    write_csv(site_data, site_filename, na = "")
  }
}

walk2(
  list(
    reminder_targets, eligible_not_enrolled, no_daily_targets,
    monthly_due_targets, protocol_review, progress_export
  ),
  c(
    "reminder_targets_3_consecutive_missed_days.csv",
    "eligible_not_enrolled_targets.csv",
    "enrolled_no_daily_submission_targets.csv",
    "monthly_report_due_targets.csv",
    "protocol_deviation_violation_review.csv",
    "participant_progress_summary.csv"
  ),
  write_site_versions
)

n_screened <- nrow(recruitment)
n_eligible <- sum(recruitment$eligibility_status == "eligible", na.rm = TRUE)
n_enrolled <- nrow(enrolment)
n_active <- sum(progress$status == "Active follow-up")
n_reached_followup <- sum(progress$status == followup_complete_label)
n_protocol_participants <- n_distinct(protocol_review$participant_id)
n_potential_violations <- sum(protocol_review$classification == "Potential violation")
n_potential_deviations <- sum(protocol_review$classification == "Potential deviation")
overall_daily_denominator <- sum(progress$expected_daily_reports)
overall_monthly_denominator <- sum(progress$expected_monthly_reports)
overall_daily_completion <- if (overall_daily_denominator > 0) {
  sum(progress$daily_reports_received) / overall_daily_denominator
} else {
  NA_real_
}
overall_monthly_completion <- if (overall_monthly_denominator > 0) {
  sum(progress$monthly_reports_received) / overall_monthly_denominator
} else {
  NA_real_
}

recruitment_start_date <- as.Date(config$study$recruitment_start_date)
recruitment_target_date <- as.Date(config$study$recruitment_target_date)
recruitment_pace_days <- config$monitoring$recruitment_pace_window_days
tracking_days <- config$monitoring$recent_daily_tracking_days
tracking_max_participants <- config$monitoring$recent_daily_tracking_max_participants
daily_completion_target <- config$monitoring$daily_completion_target
total_enrolment_target <- sum(as.integer(site_targets), na.rm = TRUE)
enrolment_remaining <- max(total_enrolment_target - n_enrolled, 0L)
pace_window_start <- max(recruitment_start_date, data_cutoff - recruitment_pace_days + 1L)
pace_window_observed_days <- max(as.integer(data_cutoff - pace_window_start) + 1L, 1L)
recent_enrolments <- sum(
  enrolment$enrollment_date >= pace_window_start &
    enrolment$enrollment_date <= data_cutoff,
  na.rm = TRUE
)
current_recruitment_pace <- recent_enrolments / pace_window_observed_days * 7
projected_completion_date <- if (enrolment_remaining == 0) {
  max(enrolment$enrollment_date, na.rm = TRUE)
} else if (is.finite(current_recruitment_pace) && current_recruitment_pace > 0) {
  data_cutoff + ceiling(enrolment_remaining / current_recruitment_pace * 7)
} else {
  as.Date(NA)
}
plan_elapsed <- pmin(
  pmax(as.numeric(data_cutoff - recruitment_start_date) /
         as.numeric(recruitment_target_date - recruitment_start_date), 0),
  1
)
planned_enrolment_to_date <- round(total_enrolment_target * plan_elapsed)
enrolment_vs_plan <- n_enrolled - planned_enrolment_to_date
expected_daily_to_date <- sum(progress$expected_daily_reports, na.rm = TRUE)
received_daily_to_date <- sum(progress$daily_reports_received, na.rm = TRUE)
operational_tracking <- op_prepare_tracking(progress, cimc, config, data_cutoff)
gap_export <- op_sort_daily(
  operational_tracking$daily_summary,
  config$monitoring$full_tracking_sort
) |>
  transmute(
    participant_id = uniqueid, organization, site, enrollment_date,
    planned_end_date, observed_end_date, observed_days, daily_received,
    missed_days, gap_episodes, longest_gap, monthly_due, monthly_received,
    monthly_missed, current_completion = daily_completion
  )
write_csv(gap_export, "participant_followup_gap_summary.csv", na = "")
write_site_versions(gap_export, "participant_followup_gap_summary.csv")
```

Data are current through `r format(data_cutoff, "%d %B %Y")`. This front page is operational: it shows recruitment flow, survey completion, and participants requiring action.

**Current source.** `r data_source_label`; staged at `r data_prepared_at`. Change `data_source.mode` in `dashboard_config.yml` to switch between development and production ingestion.

**What.** This page gives the study team a current operational picture of recruitment, enrollment, follow-up and missing reports. It covers the client-specified recruitment trajectory, screening funnel, site delivery, daily completion trend, follow-up queue, recent participant tracking, and site completion.

**How.** Records are linked by participant ID. Expected reports run from enrollment to the earliest of the configured follow-up end, data cutoff, or recorded method stop. The action lists apply the thresholds documented in `dashboard_config.yml`.

**Why.** It supports day-to-day decisions: whether recruitment is on target, whether follow-up is being sustained, and which participants may need timely contact. It is a monitoring page, not a clinical outcomes analysis.

```{r}
#| label: monitoring-kpis
#| results: asis

kpi <- function(label, value, note) {
  tags$div(
    class = "monitor-kpi",
    tags$div(class = "monitor-kpi-label", label),
    tags$div(class = "monitor-kpi-value", value),
    tags$div(class = "monitor-kpi-note", note)
  )
}

```

## Recruitment monitoring

<div class="monitor-section-kicker">Overall and by site · through `r format(data_cutoff, "%d %B %Y")`</div>

```{r}
#| label: recruitment-kpis
#| results: asis

recruitment_cards <- tags$div(
  class = "monitor-kpis",
  kpi("Enrollment target", comma(total_enrolment_target), "Across all configured sites"),
  kpi("Enrolled", comma(n_enrolled), paste(comma(enrolment_remaining), "remaining")),
  kpi(
    "Target achieved", percent(n_enrolled / total_enrolment_target, accuracy = .1),
    paste(abs(enrolment_vs_plan), if (enrolment_vs_plan < 0) "behind" else "ahead of", "planned pace")
  ),
  kpi("Current pace", paste0(number(current_recruitment_pace, accuracy = .1), "/week"),
      paste("Most recent", recruitment_pace_days, "days")),
  kpi(
    "Projected completion",
    if_else(is.na(projected_completion_date), "Not estimable", format(projected_completion_date, "%d %b %Y")),
    paste("Planned", format(recruitment_target_date, "%d %b %Y"))
  )
)

cat("```{=html}\n", as.character(recruitment_cards), "\n```\n", sep = "")
```

### Cumulative enrollment

**What it shows.** Actual cumulative enrollment against the straight-line plan implied by the configured recruitment start date, target date, and site targets.

**How it is calculated.** Enrollments are counted once on their enrollment date. The planned line rises evenly from zero to the total configured target; it is a monitoring reference rather than a statistical model.

```{r}
#| label: cumulative-enrolment
#| fig-height: 4.2
#| fig-width: 10

recruitment_weeks <- seq(
  as.Date(cut(recruitment_start_date, "week", start.on.monday = TRUE)),
  as.Date(cut(max(data_cutoff, recruitment_target_date), "week", start.on.monday = TRUE)),
  by = "week"
)

cumulative_enrolment <- tibble(week = recruitment_weeks) |>
  mutate(
    week_end = week + 6L,
    Actual = map_int(week_end, ~ sum(enrolment$enrollment_date <= min(.x, data_cutoff), na.rm = TRUE)),
    Actual = if_else(week > data_cutoff, NA_integer_, Actual),
    Planned = round(total_enrolment_target * pmin(
      pmax(as.numeric(week_end - recruitment_start_date) /
             as.numeric(recruitment_target_date - recruitment_start_date), 0),
      1
    ))
  ) |>
  select(week, Actual, Planned) |>
  pivot_longer(c(Actual, Planned), names_to = "trajectory", values_to = "participants")

ggplot(cumulative_enrolment, aes(week, participants, colour = trajectory)) +
  geom_line(linewidth = .9, na.rm = TRUE) +
  geom_point(size = 1.7, na.rm = TRUE) +
  geom_hline(yintercept = total_enrolment_target, colour = "#9aa8ad", linetype = 3) +
  scale_colour_manual(values = c(Actual = "#167c77", Planned = "#d99b21")) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, .08))) +
  labs(x = NULL, y = "Participants enrolled", colour = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

### Recruitment funnel

**What it shows.** Unique people at successive stages from screening through daily reporting and completion of the observation window.

**How it is calculated.** A person appears in every stage they have reached, so this is a cumulative funnel rather than a set of mutually exclusive groups.

**Why it helps.** The largest drop between adjacent stages identifies where recruitment or onboarding may need attention.

```{r}
#| label: recruitment-funnel
#| fig-height: 4.5
#| fig-width: 10

funnel <- tibble(
  stage = factor(
    c("Screened", "Eligible", "Enrolled", "Submitted ≥1 daily form", followup_complete_label),
    levels = rev(c("Screened", "Eligible", "Enrolled", "Submitted ≥1 daily form", followup_complete_label))
  ),
  participants = c(
    n_screened, n_eligible, n_enrolled,
    sum(progress$daily_reports_received > 0), n_reached_followup
  )
) |>
  mutate(percent_screened = participants / n_screened)

ggplot(funnel, aes(participants, stage)) +
  geom_col(fill = "#167c77", width = .66) +
  geom_text(
    aes(label = sprintf("%s  (%s)", comma(participants), percent(percent_screened, accuracy = .1))),
    hjust = -.08, size = 3.7
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, .25))) +
  labs(x = "Participants", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

### Enrollment against site targets

**What it shows.** Enrollment achieved at each site relative to its configured target.

**How it is calculated.** Enrolled participants are counted once at their enrollment site and divided by that site's target in `dashboard_config.yml`.

**Why it helps.** It distinguishes overall recruitment success from site-specific delivery. It does not measure reporting quality after enrollment.

```{r}
#| label: site-enrolment-targets
#| fig-height: 4.2
#| fig-width: 9

site_progress <- enrolment |>
  count(organization, site, name = "enrolled") |>
  mutate(
    target = as.integer(site_targets[organization]),
    target_completion = enrolled / target
  )

ggplot(site_progress, aes(target_completion, site)) +
  geom_vline(xintercept = 1, colour = "#8c4f7d", linewidth = .7) +
  geom_col(fill = "#167c77", width = .58) +
  geom_text(
    aes(label = sprintf("%s / %s  (%s)", enrolled, target, percent(target_completion, accuracy = 1))),
    hjust = -.08, size = 3.7
  ) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, .25))) +
  labs(x = "Enrollment target reached", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

### Recruitment progress by site

```{r}
#| label: site-recruitment-table
#| results: asis

site_recruitment_summary <- tibble(
  organization = names(site_targets),
  site = unname(site_labels[names(site_targets)]),
  target = as.integer(site_targets)
) |>
  left_join(
    recruitment |>
      group_by(organization) |>
      summarise(
        screened = n(),
        eligible = sum(eligibility_status == "eligible", na.rm = TRUE),
        .groups = "drop"
      ),
    by = "organization"
  ) |>
  left_join(
    enrolment |>
      group_by(organization) |>
      summarise(
        enrolled = n(),
        recent_enrolled = sum(
          enrollment_date >= pace_window_start & enrollment_date <= data_cutoff,
          na.rm = TRUE
        ),
        .groups = "drop"
      ),
    by = "organization"
  ) |>
  mutate(
    across(c(screened, eligible, enrolled, recent_enrolled), ~ replace_na(.x, 0L)),
    progress = enrolled / target,
    average_per_week = recent_enrolled / pace_window_observed_days * 7,
    remaining = pmax(target - enrolled, 0L),
    projected_end = case_when(
      remaining == 0 ~ as.Date(data_cutoff),
      average_per_week > 0 ~ data_cutoff + ceiling(remaining / average_per_week * 7),
      TRUE ~ as.Date(NA)
    )
  ) |>
  transmute(
    Site = site,
    Screened = screened,
    Eligible = eligible,
    Enrolled = enrolled,
    `Progress toward site goal` = percent(progress, accuracy = .1),
    `Average / week` = number(average_per_week, accuracy = .1),
    Remaining = remaining,
    `Projected end` = if_else(is.na(projected_end), "Not estimable", format(projected_end, "%d %b %Y"))
  )

site_table <- site_recruitment_summary |>
  kable(format = "html", align = c("l", "r", "r", "r", "r", "r", "r", "l"))
cat('<div class="monitor-table-scroll monitor-table-compact">', site_table, '</div>', sep = "\n")
```

## Daily survey completion monitoring

<div class="monitor-section-kicker">Active participants · all sites · most recent data through `r format(data_cutoff, "%d %B %Y")`</div>

```{r}
#| label: daily-completion-kpis
#| results: asis

daily_cards <- tags$div(
  class = "monitor-kpis",
  kpi("Active participants", comma(n_active), paste("Across", n_distinct(progress$site), "sites")),
  kpi("Expected to date", comma(expected_daily_to_date), "Participant-days"),
  kpi("Completed", comma(received_daily_to_date),
      paste(comma(max(expected_daily_to_date - received_daily_to_date, 0)), "missing")),
  kpi("Completion rate", if_else(is.na(overall_daily_completion), "Not yet available", percent(overall_daily_completion, accuracy = .1)),
      paste0("Target ≥", percent(daily_completion_target, accuracy = 1))),
  kpi("Needs follow-up", comma(nrow(reminder_targets)),
      paste0("≥", missed_days_threshold, " consecutive missed days"))
)
cat("```{=html}\n", as.character(daily_cards), "\n```\n", sep = "")
```

### Participant progress

**What it shows.** The current follow-up status of enrolled participants within each site.

**How it is calculated.** Status uses the configured observation window and method-discontinuation responses. “`r followup_complete_label`” means the time window elapsed; it does not require perfect questionnaire completion.

**Why it helps.** It separates participants who remain under active follow-up from those who have completed, stopped, or never begun daily reporting.

```{r}
#| label: participant-status
#| fig-height: 4.5
#| fig-width: 10

status_levels <- c(
  "Active follow-up", followup_complete_label, "Enrolled — no daily report",
  "Stopped method / follow-up ended"
)

status_by_site <- progress |>
  count(site, status) |>
  complete(site, status = status_levels, fill = list(n = 0L)) |>
  group_by(site) |>
  mutate(percent = n / sum(n), status = factor(status, levels = status_levels)) |>
  ungroup()

ggplot(status_by_site, aes(percent, site, fill = status)) +
  geom_col(width = .62) +
  geom_text(
    aes(label = if_else(percent >= .07, paste0(n, "\n", percent(percent, accuracy = 1)), "")),
    position = position_stack(vjust = .5), size = 3, lineheight = .9
  ) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = 0)) +
  scale_fill_manual(values = c("#167c77", "#8fc5c1", "#d8c8a5", "#8c4f7d")) +
  labs(x = "Percent of enrolled participants", y = NULL, fill = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

### Daily completion trend

**What it shows.** The proportion of expected daily reports actually received in each site-week.

**How it is calculated.** Each point divides received participant-days by expected participant-days among people under observation that week.

**Why it helps.** It separates growth in the enrolled cohort from genuine reporting adherence and makes site-specific implementation changes visible over time.

```{r}
#| label: weekly-daily-completion
#| fig-height: 5
#| fig-width: 10

due_calendar <- progress |>
  select(uniqueid, site, enrollment_date, observation_end_date) |>
  pmap_dfr(function(uniqueid, site, enrollment_date, observation_end_date) {
    tibble(uniqueid = uniqueid, site = site, date = seq(enrollment_date, observation_end_date, by = "day"))
  }) |>
  mutate(
    received = paste0(uniqueid, date) %in% paste0(cimc$uniqueid, cimc$date),
    week = as.Date(cut(date, "week", start.on.monday = TRUE))
  ) |>
  group_by(site, week) |>
  summarise(expected = n(), received = sum(received), completion = received / expected, .groups = "drop")

ggplot(due_calendar, aes(week, completion, colour = site, linetype = site)) +
  geom_line(linewidth = .8) +
  geom_point(size = 1.8) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(x = NULL, y = "Daily reports received / expected", colour = NULL, linetype = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

### Completion by site

```{r}
#| label: daily-completion-by-site
#| fig-height: 3.8
#| fig-width: 9

completion_by_site <- progress |>
  group_by(site) |>
  summarise(
    expected = sum(expected_daily_reports, na.rm = TRUE),
    received = sum(daily_reports_received, na.rm = TRUE),
    completion = if_else(expected > 0, received / expected, NA_real_),
    .groups = "drop"
  )

ggplot(completion_by_site, aes(completion, site, fill = completion >= daily_completion_target)) +
  geom_vline(xintercept = daily_completion_target, colour = "#67777b", linetype = 3) +
  geom_col(width = .55, show.legend = FALSE) +
  geom_text(
    aes(label = percent(completion, accuracy = .1)),
    hjust = -.12, size = 3.7
  ) +
  scale_fill_manual(values = c(`TRUE` = "#167c77", `FALSE` = "#d99b21")) +
  scale_x_continuous(
    labels = percent_format(accuracy = 1), limits = c(0, 1),
    expand = expansion(mult = c(0, .08))
  ) +
  labs(x = "Daily reports received / expected", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

<details class="dashboard-section">
<summary>Daily participant tracking — most recent `r tracking_days` days</summary>

**What it shows.** A compact recent completion calendar for the active participants most in need of attention. Green cells are received daily forms, coral cells are missed due forms, and grey cells were not due.

**How it is calculated.** Rows prioritise participants meeting the consecutive-miss rule and then those with the lowest overall daily completion. The number of displayed rows and days is configurable. Participant identifiers are shown only when publication of action lists is enabled.

```{r}
#| label: recent-participant-tracking
#| fig-height: 10
#| fig-width: 11

tracking_candidates <- progress |>
  filter(status == "Active follow-up") |>
  mutate(
    follow_up = current_consecutive_missed_days >= missed_days_threshold
  ) |>
  arrange(site, desc(follow_up), daily_completion, uniqueid) |>
  group_by(site) |>
  slice_head(n = tracking_max_participants) |>
  mutate(
    display_id = if (publish_action_lists) {
      uniqueid
    } else {
      paste0(as.character(site), " participant ", sprintf("%02d", row_number()))
    }
  ) |>
  ungroup() |>
  mutate(display_id = factor(display_id, levels = rev(display_id)))

tracking_dates <- seq(data_cutoff - tracking_days + 1L, data_cutoff, by = "day")
tracking_grid <- crossing(
  tracking_candidates |>
    select(uniqueid, site, display_id, enrollment_date, observation_end_date, follow_up),
  date = tracking_dates
) |>
  mutate(
    due = date >= enrollment_date & date <= observation_end_date,
    received = paste0(uniqueid, date) %in% paste0(cimc$uniqueid, cimc$date),
    result = case_when(
      !due ~ "Not due",
      received ~ "Received",
      TRUE ~ "Missed"
    )
  )

if (nrow(tracking_grid) == 0) {
  cat("No active participants are available for the recent tracking grid.\n")
} else {
  print(
    ggplot(tracking_grid, aes(date, display_id, fill = result)) +
      geom_tile(colour = "white", linewidth = .7, width = .92, height = .82) +
      facet_grid(site ~ ., scales = "free_y", space = "free_y") +
      scale_fill_manual(values = c(Received = "#59ad8b", Missed = "#e58d87", `Not due` = "#d9dfdf")) +
      scale_x_date(date_breaks = "1 day", date_labels = "%d", expand = expansion(add = .4)) +
      labs(x = paste(format(min(tracking_dates), "%b %Y"), "— day of month"), y = NULL, fill = NULL) +
      theme_minimal(base_size = 11) +
      theme(
        legend.position = "top", panel.grid = element_blank(),
        axis.text.x = element_text(size = 8)
      )
  )
}
```

</details>

<details class="dashboard-section">
<summary>Monthly participant tracking — all study months</summary>

**What it shows.** One cell per participant and calendar month since recruitment began, separated by study site. Purple indicates a received monthly section and amber indicates a section that was due but missing.

**How it is calculated.** Monthly due dates use the configured day of month and each participant's observed follow-up interval. Rows with the most missing monthly sections appear first within each site.

```{r}
#| label: monthly-participant-tracking
#| fig-height: 16
#| fig-width: 11

monthly_tracking_summary <- operational_tracking$monthly_summary |>
  arrange(site, desc(monthly_missed), monthly_completion, uniqueid) |>
  group_by(site) |>
  mutate(
    site_rank = row_number(),
    display_id = if (publish_action_lists) {
      uniqueid
    } else {
      paste0(as.character(site), " participant ", sprintf("%03d", site_rank))
    }
  ) |>
  ungroup()

monthly_tracking_grid <- operational_tracking$monthly_grid |>
  left_join(
    monthly_tracking_summary |> select(uniqueid, display_id),
    by = "uniqueid"
  ) |>
  mutate(display_id = factor(display_id, levels = rev(monthly_tracking_summary$display_id)))

if (nrow(monthly_tracking_grid) == 0) {
  cat("No enrolled participants are available for monthly tracking.\n")
} else {
  print(
    ggplot(monthly_tracking_grid, aes(month, display_id, fill = result)) +
      geom_tile(colour = "white", linewidth = .45, width = 25, height = .82) +
      facet_grid(site ~ ., scales = "free_y", space = "free_y") +
      scale_fill_manual(
        values = c(
          `Monthly received` = "#7763a8",
          `Monthly missing` = "#e2ac43",
          `Not yet due` = "#edf1f2",
          `Not enrolled / not due` = "#d9dfdf",
          `Follow-up ended` = "#b9c1c3"
        ),
        drop = FALSE
      ) +
      scale_x_date(date_breaks = "1 month", date_labels = "%b\n%Y", expand = expansion(add = 12)) +
      labs(x = NULL, y = NULL, fill = NULL) +
      theme_minimal(base_size = 10) +
      theme(
        legend.position = "top", panel.grid = element_blank(),
        axis.text.y = element_text(size = 7)
      )
  )
}
```

</details>

<details class="dashboard-section">
<summary>Daily follow-up queues by site</summary>

```{r}
#| label: front-follow-up-queue
#| results: asis

if (nrow(reminder_targets) == 0) {
  cat("No active participant currently meets the configured consecutive-miss threshold.\n")
} else if (publish_action_lists) {
  for (site_name in unname(site_labels)) {
    site_queue <- reminder_targets |>
      filter(as.character(site) == site_name) |>
      slice_head(n = config$monitoring$action_list_preview_rows) |>
      transmute(
        `Participant ID` = participant_id,
        `Reason flagged` = paste(current_consecutive_missed_days, "consecutive missed days"),
        `Last report` = last_report_date,
        `Completion` = percent(daily_completion, accuracy = .1)
      )
    cat("#### ", site_name, " — ", nrow(site_queue), " participant(s)\n\n", sep = "")
    cat('<div class="monitor-table-scroll monitor-table-compact">',
        kable(site_queue, format = "html", align = c("l", "l", "l", "r")),
        '</div>', sep = "\n")
  }
} else {
  follow_up_summary <- reminder_targets |>
    count(site, name = "Participants") |>
    rename(Site = site) |>
    kable(format = "html", align = c("l", "r"))
  cat("Participant identifiers are hidden in the rendered production site. The protected reminder CSV contains the operational queue.\n")
  cat('<div class="monitor-table-scroll monitor-table-compact">', follow_up_summary, '</div>', sep = "\n")
}
```

</details>

<details class="dashboard-section">
<summary>Monthly follow-up queues by site</summary>

```{r}
#| label: front-monthly-follow-up-queue
#| results: asis

if (nrow(monthly_due_targets) == 0) {
  cat("No participant currently has an overdue monthly section under the configured grace period.\n")
} else if (publish_action_lists) {
  for (site_name in unname(site_labels)) {
    site_queue <- monthly_due_targets |>
      filter(as.character(site) == site_name) |>
      slice_head(n = config$monitoring$action_list_preview_rows) |>
      transmute(
        `Participant ID` = participant_id,
        `Monthly sections missing` = monthly_reports_missing,
        `Last monthly due date` = last_monthly_report_due,
        `Reminder method` = reminder_method
      )
    cat("#### ", site_name, " — ", nrow(site_queue), " participant(s)\n\n", sep = "")
    cat('<div class="monitor-table-scroll monitor-table-compact">',
        kable(site_queue, format = "html", align = c("l", "r", "l", "l")),
        '</div>', sep = "\n")
  }
} else {
  monthly_queue_summary <- monthly_due_targets |>
    count(site, name = "Participants") |>
    rename(Site = site) |>
    kable(format = "html", align = c("l", "r"))
  cat("Participant identifiers are hidden in the rendered production site. The protected monthly reminder CSVs contain the site queues.\n")
  cat('<div class="monitor-table-scroll monitor-table-compact">', monthly_queue_summary, '</div>', sep = "\n")
}
```

</details>

## Potential protocol deviations and violations

**What it shows.** This section screens linked study forms for records that may represent a protocol deviation or violation. The supplied rules include CIMC reports without enrollment, missing programme start dates, reports dated before enrollment, duplicate participant-days, duplicate enrollments, and enrollments without recruitment records.

**How it is calculated.** Exact participant IDs and recorded dates are compared across recruitment, enrollment, and CIMC submissions. Each rule and its provisional classification are controlled in `dashboard_config.yml`. CIMC submissions without a valid linked programme start remain in this monitoring register but are excluded from symptom and cycle analyses.

**Why it helps.** A linkage problem should create an actionable signal rather than prevent the dashboard from rendering. These are **potential** events: the dashboard does not determine seriousness, causality, or reportability. The study team must verify source records and adjudicate each flag under the approved protocol and deviation-management procedures.

```{r}
#| label: protocol-monitoring-summary
#| results: asis

protocol_cards <- tags$div(
  class = "monitor-kpis",
  kpi("Potential violations", comma(n_potential_violations), "Flagged records requiring review"),
  kpi("Potential deviations", comma(n_potential_deviations), "Flagged records requiring review"),
  kpi("Participants flagged", comma(n_protocol_participants), "Unique IDs across all flags")
)
cat("```{=html}\n", as.character(protocol_cards), "\n```\n", sep = "")

if (nrow(protocol_summary) == 0) {
  cat("No potential protocol deviations or violations were detected by the configured checks.\n")
} else {
  summary_table <- protocol_summary |>
    rename(
      Classification = classification,
      `Automated screening flag` = issue,
      Participants = participants,
      `Flagged records` = flagged_records
    ) |>
    kable(format = "html", align = c("l", "l", "r", "r"))
  cat('<div class="monitor-table-scroll protocol-summary-table">', summary_table, '</div>', sep = "\n")
}
```

The participant-level review file is regenerated on every render as `protocol_deviation_violation_review.csv`. In production, it remains in the protected project folder and is not copied into the publishable `docs/` site unless publication of action lists has been explicitly enabled.

```{r}
#| label: protocol-monitoring-preview
#| results: asis

if (publish_action_lists && nrow(protocol_review) > 0) {
  protocol_preview <- protocol_review |>
    slice_head(n = config$monitoring$action_list_preview_rows) |>
    transmute(
      `Participant ID` = participant_id,
      Classification = classification,
      Issue = issue,
      Form = source_form,
      Date = record_date,
      Site = site,
      Status = review_status
    ) |>
    kable(format = "html", align = c("l", "l", "l", "l", "l", "l", "l"))
  cat('<div class="monitor-table-scroll">', protocol_preview, '</div>', sep = "\n")
} else if (!publish_action_lists && nrow(protocol_review) > 0) {
  cat("Participant-level details are hidden from the rendered production site. Use the protected review CSV for follow-up.\n")
}
```

## Data quality and analysis checks

**What it shows.** Automated structural checks for duplicate records, dates before programme start, skip-logic inconsistencies, and contradictory monthly responses. Results are shown for the study overall and for each operational site.

**Why it helps.** Site-specific counts show where a form, training, linkage, or submission-process problem should be investigated without requiring a separate data-quality chapter.

```{r}
#| label: front-data-quality
#| results: asis

quality_daily <- read_csv(
  config$files$daily_data,
  col_types = cols(participant_id = col_character()),
  show_col_types = FALSE
) |>
  mutate(
    participant_id = as.character(participant_id),
    report_date = as.Date(as.character(report_date)),
    programme_start_date = as.Date(as.character(programme_start_date))
  ) |>
  left_join(
    enrolment |> transmute(participant_id = uniqueid, site = as.character(site)),
    by = "participant_id"
  )

quality_monthly <- read_csv(
  config$files$monthly_data,
  col_types = cols(participant_id = col_character()),
  show_col_types = FALSE
) |>
  mutate(participant_id = as.character(participant_id)) |>
  left_join(
    enrolment |> transmute(participant_id = uniqueid, site = as.character(site)),
    by = "participant_id"
  )

quality_by_scope <- bind_rows(
  op_quality_checks(quality_daily, quality_monthly, config$fields$pain_locations, config) |>
    mutate(Scope = "All sites"),
  map_dfr(unname(site_labels), function(site_name) {
    op_quality_checks(
      quality_daily |> filter(site == site_name),
      quality_monthly |> filter(site == site_name),
      config$fields$pain_locations,
      config
    ) |>
      mutate(Scope = site_name)
  })
) |>
  select(Scope, Check, Issues)

quality_totals <- quality_by_scope |>
  group_by(Scope) |>
  summarise(Issues = sum(Issues), .groups = "drop")

quality_cards <- tags$div(
  class = "monitor-kpis",
  lapply(seq_len(nrow(quality_totals)), function(index) {
    kpi(
      quality_totals$Scope[[index]],
      comma(quality_totals$Issues[[index]]),
      "Automated structural issues"
    )
  })
)
cat("```{=html}\n", as.character(quality_cards), "\n```\n", sep = "")
```

<details class="dashboard-section">
<summary>Detailed data-quality checks by site</summary>

```{r}
#| label: front-data-quality-detail
#| results: asis

quality_table <- quality_by_scope |>
  pivot_wider(names_from = Scope, values_from = Issues) |>
  select(Check, `All sites`, all_of(unname(site_labels))) |>
  kable(format = "html", align = c("l", rep("r", length(site_labels) + 1L)))
cat('<div class="monitor-table-scroll monitor-table-compact">', quality_table, '</div>', sep = "\n")
```

</details>

## Completion-pattern UpSet chart

**What it shows.** Exact combinations of reporting and follow-up milestones reached by participants.

**How it is calculated.** The upper bars count participants in each combination; filled dots identify the milestones included in that combination.

**Why it helps.** It shows whether apparent progress is driven by complete follow-up, strong daily adherence, monthly completion, or only one of those elements.

```{r}
#| label: completion-upset
#| fig-height: 7
#| fig-width: 11

completion_sets <- progress |>
  transmute(
    participant_id = uniqueid,
    `Started daily reporting` = daily_reports_received > 0,
    `At least 80% daily` = daily_completion >= config$monitoring$good_daily_completion_threshold,
    `All due monthly` = expected_monthly_reports > 0 & monthly_reports_received >= expected_monthly_reports,
    !!followup_complete_label := planned_end_date <= data_cutoff
  )

set_columns <- setdiff(names(completion_sets), "participant_id")
intersection_counts <- completion_sets |>
  count(across(all_of(set_columns)), name = "participants") |>
  arrange(desc(participants)) |>
  slice_head(n = config$display$upset_max_intersections) |>
  mutate(intersection_id = row_number())

matrix_data <- intersection_counts |>
  pivot_longer(all_of(set_columns), names_to = "milestone", values_to = "included") |>
  mutate(
    milestone = factor(milestone, levels = rev(set_columns)),
    milestone_number = as.numeric(milestone)
  )

connection_data <- matrix_data |>
  filter(included) |>
  group_by(intersection_id) |>
  summarise(ymin = min(milestone_number), ymax = max(milestone_number), .groups = "drop")

upset_bars <- ggplot(intersection_counts, aes(intersection_id, participants)) +
  geom_col(fill = "#167c77", width = .68) +
  geom_text(aes(label = participants), vjust = -.3, size = 3.3) +
  scale_x_continuous(breaks = intersection_counts$intersection_id, labels = NULL) +
  scale_y_continuous(expand = expansion(mult = c(0, .14))) +
  labs(x = NULL, y = "Participants") +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank())

upset_matrix <- ggplot(matrix_data, aes(intersection_id, milestone_number)) +
  geom_segment(
    data = connection_data,
    aes(x = intersection_id, xend = intersection_id, y = ymin, yend = ymax),
    inherit.aes = FALSE, colour = "#455553", linewidth = .6
  ) +
  geom_point(colour = "#d5dddc", size = 3) +
  geom_point(data = filter(matrix_data, included), colour = "#167c77", size = 3.5) +
  scale_x_continuous(breaks = intersection_counts$intersection_id) +
  scale_y_continuous(
    breaks = seq_along(levels(matrix_data$milestone)),
    labels = levels(matrix_data$milestone)
  ) +
  labs(x = "Exact completion-pattern intersection", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid = element_blank())

upset_bars / upset_matrix + plot_layout(heights = c(1.7, 1))
```

## Action lists

**What they contain.** Participant-level lists for specific follow-up actions, plus a complete operational progress file.

**How they are produced.** The CSVs are rebuilt from the current data every time the dashboard renders using the configured thresholds.

**Why they help.** They turn dashboard signals into practical worklists. They contain operational identifiers and dummy contact details here; production access should follow the study's role-based confidentiality controls.

```{r}
#| label: action-downloads
#| results: asis

download_card <- function(title, count, file, detail) {
  action <- if (publish_action_lists) {
    tags$div(
      class = "monitor-download-links",
      tags$a(href = file, download = file, "Combined"),
      lapply(names(site_labels), function(site_code) {
        site_file <- str_replace(file, "\\.csv$", paste0("_", site_code, ".csv"))
        tags$a(
          href = site_file, download = site_file,
          unname(site_labels[[site_code]])
        )
      })
    )
  } else {
    tags$div(
      class = "small text-muted",
      "Generated locally; publication is disabled for production data."
    )
  }
  tags$div(
    class = "monitor-download",
    tags$strong(paste0(title, " — ", count)),
    tags$div(class = "small text-muted", detail),
    action
  )
}

downloads <- tags$div(
  class = "monitor-downloads",
  download_card(
    "Consecutive missed daily reports", nrow(reminder_targets),
    "reminder_targets_3_consecutive_missed_days.csv",
    paste0("Active participants missing at least ", missed_days_threshold, " consecutive due days")
  ),
  download_card(
    "Eligible but not enrolled", nrow(eligible_not_enrolled),
    "eligible_not_enrolled_targets.csv",
    paste0("Eligible for at least ", config$monitoring$eligible_not_enrolled_after_days, " days without an enrollment record")
  ),
  download_card(
    "Enrolled with no daily report", nrow(no_daily_targets),
    "enrolled_no_daily_submission_targets.csv",
    "Enrolled participants who have not started daily reporting"
  ),
  download_card(
    "Overdue monthly sections", nrow(monthly_due_targets),
    "monthly_report_due_targets.csv",
    "Calendar-month sections still missing after the configured grace period"
  ),
  download_card(
    "Protocol deviation/violation review", nrow(protocol_review),
    "protocol_deviation_violation_review.csv",
    "Automated cross-form flags requiring study-team verification and adjudication"
  ),
  download_card(
    "Full participant progress", nrow(progress),
    "participant_progress_summary.csv",
    "One operational progress row per enrolled participant"
  ),
  download_card(
    "Ranked participant gap summary", nrow(gap_export),
    "participant_followup_gap_summary.csv",
    "Full-protocol daily gaps and monthly completion counts"
  )
)

cat("```{=html}\n", as.character(downloads), "\n```\n", sep = "")
```

<details class="dashboard-section">
<summary>Current consecutive-miss reminder lists by site</summary>

```{r}
#| label: reminder-target-preview
#| results: asis

if (publish_action_lists) {
  for (site_name in unname(site_labels)) {
    preview_table <- reminder_targets |>
      filter(as.character(site) == site_name) |>
      slice_head(n = config$monitoring$action_list_preview_rows) |>
      transmute(
        `Participant ID` = participant_id,
        `Missed days` = current_consecutive_missed_days,
        `Last report` = last_report_date,
        `Reminder method` = reminder_method,
        Contact = reminder_contact,
        `Daily completion` = percent(daily_completion, accuracy = .1)
      ) |>
      kable(format = "html", align = c("l", "r", "l", "l", "l", "r"))
    cat("#### ", site_name, "\n\n", sep = "")
    cat('<div class="monitor-table-scroll">', preview_table, '</div>', sep = "\n")
  }
} else {
  cat("Participant-level reminder lists are available in the protected combined and site-specific CSV files.\n")
}
```

</details>

## Monitoring definitions

- **Expected daily reports** run from enrollment through the earliest of the configured follow-up day (`r expected_study_days`), the data cutoff, or a recorded method stop date.
- **Monthly reports expected** are calendar-month sections due on configured day `r monthly_due_day` of a month within that observed interval. The supplied setting matches the revised CIMC form.
- **Current consecutive missed days** count backwards from the participant's latest due day. A submitted form breaks the streak.
- **`r followup_complete_label`** describes elapsed follow-up time, not questionnaire adherence.
- All thresholds and site targets are editable in `dashboard_config.yml`.
