---
title: "Recruitment and participant progress"
subtitle: "Operational monitoring dashboard"
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: monitoring-setup

library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(ggplot2)
library(scales)
library(knitr)
library(yaml)
library(htmltools)
library(patchwork)

config <- read_yaml("dashboard_config.yml")
id_column_type <- cols(uniqueid = col_character())
recruitment <- read_csv(
  config$files$recruitment, col_types = id_column_type, show_col_types = FALSE
)
enrolment <- read_csv(
  config$files$enrolment, col_types = id_column_type, show_col_types = FALSE
)
cimc <- read_csv(
  config$files$cimc, col_types = id_column_type, show_col_types = FALSE
)
refresh_metadata <- read_csv(config$files$refresh_metadata, show_col_types = FALSE)

data_mode <- tolower(config$data_source$mode)
mode_settings <- config$data_source[[data_mode]]
publish_action_lists <- isTRUE(mode_settings$publish_action_lists_in_rendered_site)
data_source_label <- if (data_mode == "production") "Kobo API production data" else "Linked dummy development data"
data_prepared_at <- first(refresh_metadata$prepared_at_utc)

site_labels <- unlist(config$labels$sites)
site_targets <- unlist(config$study$site_targets)
data_cutoff <- as.Date(first(refresh_metadata$effective_data_cutoff))
expected_study_days <- config$study$expected_daily_reports
missed_days_threshold <- config$monitoring$consecutive_missed_days
monthly_due_day <- config$study$monthly_due_day
followup_complete_label <- paste0("Reached day ", expected_study_days)

recruitment <- recruitment |>
  mutate(
    uniqueid = as.character(uniqueid),
    recruitment_date = as.Date(recruitment_date),
    planned_enrollment_date = as.Date(as.character(enrollment_date)),
    phone = as.character(phone),
    email = as.character(email),
    site = factor(unname(site_labels[organization]), levels = unname(site_labels))
  )

enrolment <- enrolment |>
  mutate(
    uniqueid = as.character(uniqueid),
    enrollment_date = as.Date(as.character(enrollment_date)),
    contraception_start_date = as.Date(as.character(contraception_start_date)),
    phone = as.character(phone),
    email = as.character(email),
    daily_reminder_method = as.character(daily_reminder_method),
    missed_days_reminder_method = as.character(missed_days_reminder_method),
    site = factor(unname(site_labels[organization]), levels = unname(site_labels))
  )

# Preserve every submitted record for protocol monitoring, but use one current
# record per participant for operational calculations. Kobo's numeric `_id`
# increases with each submission; the highest ID is treated as the current row.
canonical_latest_record <- function(data) {
  source_order <- seq_len(nrow(data))
  kobo_order <- if ("_id" %in% names(data)) {
    suppressWarnings(as.numeric(data[["_id"]]))
  } else {
    rep(NA_real_, nrow(data))
  }
  data |>
    mutate(.canonical_order = coalesce(kobo_order, as.numeric(source_order))) |>
    arrange(uniqueid, desc(.canonical_order)) |>
    distinct(uniqueid, .keep_all = TRUE) |>
    select(-.canonical_order)
}

recruitment_records <- recruitment
enrolment_records <- enrolment
recruitment <- canonical_latest_record(recruitment_records)
enrolment <- canonical_latest_record(enrolment_records)

cimc <- cimc |>
  mutate(
    uniqueid = as.character(uniqueid),
    date = as.Date(as.character(date)),
    method_stop_date = as.Date(as.character(QB))
  ) |>
  left_join(
    enrolment |>
      transmute(
        uniqueid, organization, site, enrollment_date,
        programme_start_date = contraception_start_date,
        enrolment_record_present = TRUE
      ),
    by = "uniqueid"
  )

# Automated protocol flags are screening signals for study-team adjudication.
# They deliberately use exact participant-ID matching so linkage problems are
# visible rather than silently corrected.
protocol_rules <- config$protocol_monitoring$rules
empty_protocol_review <- tibble(
  participant_id = character(), classification = character(), flag_code = character(),
  issue = character(), source_form = character(), record_date = as.Date(character()),
  site = character(), records = integer(), detail = character(),
  suggested_action = character(), review_status = character()
)

make_protocol_flags <- function(data, code, issue, source_form, detail, suggested_action) {
  rule <- protocol_rules[[code]]
  if (is.null(rule) || !isTRUE(rule$enabled) || nrow(data) == 0) {
    return(empty_protocol_review)
  }
  severity <- tolower(rule$severity)
  if (!severity %in% c("deviation", "violation")) {
    stop("Protocol rule ", code, " severity must be 'deviation' or 'violation'.")
  }
  data |>
    transmute(
      participant_id = as.character(uniqueid),
      classification = if_else(
        severity == "violation", "Potential violation", "Potential deviation"
      ),
      flag_code = code,
      issue = issue,
      source_form = source_form,
      record_date = as.Date(record_date),
      site = as.character(site),
      records = as.integer(records),
      detail = detail,
      suggested_action = suggested_action,
      review_status = "Needs review"
    )
}

protocol_review <- bind_rows(
  make_protocol_flags(
    cimc |>
      filter(is.na(enrolment_record_present)) |>
      distinct(uniqueid, date, .keep_all = TRUE) |>
      transmute(uniqueid, record_date = date, site, records = 1L),
    "cimc_without_enrolment",
    "CIMC submission has no matching enrolment record",
    "CIMC",
    "The participant ID was present in CIMC but absent from enrolment.",
    "Verify the ID and enrolment history; document and adjudicate the event."
  ),
  make_protocol_flags(
    enrolment |>
      filter(is.na(contraception_start_date)) |>
      transmute(uniqueid, record_date = enrollment_date, site, records = 1L),
    "missing_programme_start_date",
    "Enrolment has no valid programme start date",
    "Enrolment",
    "A programme start date is required to define follow-up and cycle timing.",
    "Verify the source record and correct it through the approved data process."
  ),
  make_protocol_flags(
    cimc |>
      filter(!is.na(enrollment_date), !is.na(date), date < enrollment_date) |>
      distinct(uniqueid, date, .keep_all = TRUE) |>
      transmute(uniqueid, record_date = date, site, records = 1L),
    "cimc_before_enrolment",
    "CIMC report is dated before enrolment",
    "CIMC",
    "The report date precedes the linked participant's enrolment date.",
    "Check form dates, time zone, participant ID, and whether follow-up began early."
  ),
  make_protocol_flags(
    cimc |>
      count(uniqueid, date, site, name = "records") |>
      filter(records > 1) |>
      transmute(uniqueid, record_date = date, site, records),
    "duplicate_cimc_participant_date",
    "More than one CIMC submission for a participant-day",
    "CIMC",
    "Multiple submissions share the same participant ID and report date.",
    "Determine whether this is a correction, duplicate, or additional submission."
  ),
  make_protocol_flags(
    enrolment_records |>
      count(uniqueid, name = "records") |>
      filter(records > 1) |>
      left_join(
        enrolment |>
          transmute(uniqueid, record_date = enrollment_date, site),
        by = "uniqueid"
      ) |>
      transmute(uniqueid, record_date, site, records),
    "duplicate_enrolment_participant",
    "More than one enrolment submission for a participant",
    "Enrolment",
    "Multiple enrolment records share the same participant ID.",
    "Verify whether the later record is an authorised correction and adjudicate the duplicate."
  ),
  make_protocol_flags(
    enrolment |>
      anti_join(recruitment |> distinct(uniqueid), by = "uniqueid") |>
      transmute(uniqueid, record_date = enrollment_date, site, records = 1L),
    "enrolment_without_recruitment",
    "Enrolment has no matching recruitment record",
    "Enrolment",
    "The participant ID was present in enrolment but absent from recruitment.",
    "Verify recruitment history and participant ID; adjudicate against the protocol."
  )
) |>
  arrange(factor(classification, c("Potential violation", "Potential deviation")),
          issue, participant_id, record_date)

protocol_summary <- protocol_review |>
  group_by(classification, issue) |>
  summarise(
    participants = n_distinct(participant_id),
    flagged_records = sum(records),
    .groups = "drop"
  ) |>
  arrange(factor(classification, c("Potential violation", "Potential deviation")),
          desc(participants), issue)

method_stops <- cimc |>
  filter(QA == 0, !is.na(method_stop_date)) |>
  group_by(uniqueid) |>
  summarise(method_stop_date = min(method_stop_date), .groups = "drop")

daily_counts <- cimc |>
  distinct(uniqueid, date) |>
  group_by(uniqueid) |>
  summarise(
    daily_reports_received = n(),
    first_report_date = min(date),
    last_report_date = max(date),
    .groups = "drop"
  )

monthly_counts <- cimc |>
  filter(monthly_report_due == "yes") |>
  distinct(uniqueid, date) |>
  count(uniqueid, name = "monthly_reports_received")

count_monthly_due_dates <- function(start_date, end_date) {
  if (is.na(start_date) || is.na(end_date) || end_date < start_date) return(0L)
  sum(as.integer(format(seq(start_date, end_date, by = "day"), "%d")) == monthly_due_day)
}

last_monthly_due_date <- function(start_date, end_date) {
  if (is.na(start_date) || is.na(end_date) || end_date < start_date) return(as.Date(NA))
  dates <- seq(start_date, end_date, by = "day")
  dates <- dates[as.integer(format(dates, "%d")) == monthly_due_day]
  if (length(dates) == 0) as.Date(NA) else max(dates)
}

progress <- enrolment |>
  left_join(method_stops, by = "uniqueid") |>
  left_join(daily_counts, by = "uniqueid") |>
  left_join(monthly_counts, by = "uniqueid") |>
  mutate(
    planned_end_date = enrollment_date + expected_study_days - 1L,
    observation_end_date = pmin(
      planned_end_date, data_cutoff, coalesce(method_stop_date, data_cutoff),
      na.rm = TRUE
    ),
    expected_daily_reports = pmax(0L, as.integer(observation_end_date - enrollment_date) + 1L),
    daily_reports_received = replace_na(daily_reports_received, 0L),
    monthly_reports_received = replace_na(monthly_reports_received, 0L),
    expected_monthly_reports = map2_int(
      enrollment_date, observation_end_date, count_monthly_due_dates
    ),
    last_monthly_report_due = as.Date(map2_dbl(
      enrollment_date, observation_end_date,
      ~ as.numeric(last_monthly_due_date(.x, .y))
    ), origin = "1970-01-01"),
    daily_completion = if_else(
      expected_daily_reports > 0,
      daily_reports_received / expected_daily_reports,
      NA_real_
    ),
    monthly_completion = if_else(
      expected_monthly_reports > 0,
      monthly_reports_received / expected_monthly_reports,
      NA_real_
    ),
    status = case_when(
      !is.na(method_stop_date) & method_stop_date <= data_cutoff ~ "Stopped method / follow-up ended",
      planned_end_date <= data_cutoff ~ followup_complete_label,
      daily_reports_received == 0 ~ "Enrolled — no daily report",
      TRUE ~ "Active follow-up"
    )
  )

current_missing_streak <- function(start_date, end_date, received_dates) {
  if (is.na(start_date) || is.na(end_date) || end_date < start_date) return(0L)
  due_dates <- seq(start_date, end_date, by = "day")
  missing <- !due_dates %in% received_dates
  streak <- rle(rev(missing))
  if (length(streak$values) == 0 || !streak$values[[1]]) 0L else streak$lengths[[1]]
}

received_dates_by_id <- split(cimc$date, cimc$uniqueid)
progress$current_consecutive_missed_days <- map2_int(
  progress$uniqueid,
  progress$observation_end_date,
  function(uid, end_date) {
    received <- received_dates_by_id[[uid]]
    if (is.null(received)) received <- as.Date(character())
    current_missing_streak(
      progress$enrollment_date[progress$uniqueid == uid], end_date, received
    )
  }
)

progress <- progress |>
  mutate(
    preferred_missed_reminder = case_when(
      !is.na(missed_days_reminder_method) ~ missed_days_reminder_method,
      str_detect(coalesce(daily_reminder_method, ""), "whatsapp") ~ "whatsapp",
      str_detect(coalesce(daily_reminder_method, ""), "text_message_sms") ~ "text_message_sms",
      str_detect(coalesce(daily_reminder_method, ""), "email") ~ "email",
      TRUE ~ daily_reminder_method
    ),
    reminder_contact = case_when(
      preferred_missed_reminder == "email" ~ email,
      preferred_missed_reminder %in% c("whatsapp", "text_message_sms") ~ phone,
      TRUE ~ coalesce(phone, email)
    )
  )

# Operational exports are regenerated whenever the dashboard is rendered.
reminder_targets <- progress |>
  filter(
    status == "Active follow-up",
    current_consecutive_missed_days >= missed_days_threshold
  ) |>
  transmute(
    participant_id = uniqueid, organization, site,
    current_consecutive_missed_days, last_report_date,
    reminder_method = preferred_missed_reminder, reminder_contact,
    daily_completion
  ) |>
  arrange(desc(current_consecutive_missed_days), site, participant_id)

eligible_not_enrolled <- recruitment |>
  filter(
    eligibility_status == "eligible",
    as.integer(data_cutoff - recruitment_date) >= config$monitoring$eligible_not_enrolled_after_days
  ) |>
  anti_join(enrolment, by = "uniqueid") |>
  transmute(
    participant_id = uniqueid, organization, site, recruitment_date,
    days_since_recruitment = as.integer(data_cutoff - recruitment_date),
    planned_enrollment_date, phone, email, reminder, notes
  ) |>
  arrange(desc(days_since_recruitment), site)

no_daily_targets <- progress |>
  filter(
    daily_reports_received == 0,
    as.integer(data_cutoff - enrollment_date) >= config$monitoring$no_daily_report_after_days,
    status != "Stopped method / follow-up ended"
  ) |>
  transmute(
    participant_id = uniqueid, organization, site, enrollment_date,
    days_since_enrollment = as.integer(data_cutoff - enrollment_date),
    daily_reminder_method, phone, email
  ) |>
  arrange(desc(days_since_enrollment), site)

monthly_due_targets <- progress |>
  filter(
    expected_monthly_reports > monthly_reports_received,
    !is.na(last_monthly_report_due),
    as.integer(data_cutoff - last_monthly_report_due) >= config$monitoring$monthly_report_grace_days
  ) |>
  transmute(
    participant_id = uniqueid, organization, site,
    expected_monthly_reports, monthly_reports_received,
    monthly_reports_missing = expected_monthly_reports - monthly_reports_received,
    last_monthly_report_due, reminder_method = preferred_missed_reminder,
    reminder_contact
  ) |>
  arrange(desc(monthly_reports_missing), site, participant_id)

write_csv(reminder_targets, "reminder_targets_3_consecutive_missed_days.csv", na = "")
write_csv(eligible_not_enrolled, "eligible_not_enrolled_targets.csv", na = "")
write_csv(no_daily_targets, "enrolled_no_daily_submission_targets.csv", na = "")
write_csv(monthly_due_targets, "monthly_report_due_targets.csv", na = "")
write_csv(protocol_review, "protocol_deviation_violation_review.csv", na = "")
write_csv(
  progress |>
    transmute(
      participant_id = uniqueid, organization, site, enrollment_date,
      planned_end_date, status, daily_reports_received, expected_daily_reports,
      daily_completion, monthly_reports_received, expected_monthly_reports,
      monthly_completion, current_consecutive_missed_days, last_report_date,
      method_stop_date
    ),
  "participant_progress_summary.csv", na = ""
)

n_screened <- nrow(recruitment)
n_eligible <- sum(recruitment$eligibility_status == "eligible", na.rm = TRUE)
n_enrolled <- nrow(enrolment)
n_active <- sum(progress$status == "Active follow-up")
n_reached_followup <- sum(progress$status == followup_complete_label)
n_protocol_participants <- n_distinct(protocol_review$participant_id)
n_potential_violations <- sum(protocol_review$classification == "Potential violation")
n_potential_deviations <- sum(protocol_review$classification == "Potential deviation")
overall_daily_completion <- sum(progress$daily_reports_received) / sum(progress$expected_daily_reports)
overall_monthly_completion <- sum(progress$monthly_reports_received) / sum(progress$expected_monthly_reports)
```

Data are current through `r format(data_cutoff, "%d %B %Y")`. This front page is operational: it shows recruitment flow, follow-up coverage, and participants requiring action. Counts use linked participant IDs across the recruitment, enrolment, and CIMC forms.

**Current source.** `r data_source_label`; staged at `r data_prepared_at`. Change `data_source.mode` in `dashboard_config.yml` to switch between development and production ingestion.

**What.** This page gives the study team a current operational picture of recruitment, enrolment, follow-up and missing reports.

**How.** Records are linked by participant ID. Expected reports run from enrolment to the earliest of the configured follow-up end, data cutoff, or recorded method stop. The action lists apply the thresholds documented in `dashboard_config.yml`.

**Why.** It supports day-to-day decisions: whether recruitment is on target, whether follow-up is being sustained, and which participants may need timely contact. It is a monitoring page, not a clinical outcomes analysis.

```{r}
#| label: monitoring-kpis
#| results: asis

kpi <- function(label, value, note) {
  tags$div(
    class = "monitor-kpi",
    tags$div(class = "monitor-kpi-label", label),
    tags$div(class = "monitor-kpi-value", value),
    tags$div(class = "monitor-kpi-note", note)
  )
}

cards <- tags$div(
  class = "monitor-kpis",
  kpi("Screened", comma(n_screened), "Recruitment forms"),
  kpi("Eligible", comma(n_eligible), percent(n_eligible / n_screened, accuracy = .1)),
  kpi("Enrolled", comma(n_enrolled), paste0(percent(n_enrolled / n_eligible, accuracy = .1), " of eligible")),
  kpi("Active follow-up", comma(n_active), paste("Before day", expected_study_days)),
  kpi(followup_complete_label, comma(n_reached_followup), "Observation window reached"),
  kpi("Daily completion", percent(overall_daily_completion, accuracy = .1), "Reports received / expected"),
  kpi("Monthly completion", percent(overall_monthly_completion, accuracy = .1), "Due monthly sections"),
  kpi("Reminder targets", comma(nrow(reminder_targets)), paste0("≥", missed_days_threshold, " consecutive missed days")),
  kpi("Protocol flags", comma(nrow(protocol_review)), paste(comma(n_protocol_participants), "participant(s)")),
  kpi("Data source", str_to_title(data_mode), data_prepared_at)
)

cat("```{=html}\n", as.character(cards), "\n```\n", sep = "")
```

## Potential protocol deviations and violations

**What it shows.** This section screens linked study forms for records that may represent a protocol deviation or violation. The supplied rules include CIMC reports without enrolment, missing programme start dates, reports dated before enrolment, duplicate participant-days, duplicate enrolments, and enrolments without recruitment records.

**How it is calculated.** Exact participant IDs and recorded dates are compared across recruitment, enrolment, and CIMC submissions. Each rule and its provisional classification are controlled in `dashboard_config.yml`. CIMC submissions without a valid linked programme start remain in this monitoring register but are excluded from symptom and cycle analyses.

**Why it helps.** A linkage problem should create an actionable signal rather than prevent the dashboard from rendering. These are **potential** events: the dashboard does not determine seriousness, causality, or reportability. The study team must verify source records and adjudicate each flag under the approved protocol and deviation-management procedures.

```{r}
#| label: protocol-monitoring-summary
#| results: asis

protocol_cards <- tags$div(
  class = "monitor-kpis",
  kpi("Potential violations", comma(n_potential_violations), "Flagged records requiring review"),
  kpi("Potential deviations", comma(n_potential_deviations), "Flagged records requiring review"),
  kpi("Participants flagged", comma(n_protocol_participants), "Unique IDs across all flags")
)
cat("```{=html}\n", as.character(protocol_cards), "\n```\n", sep = "")

if (nrow(protocol_summary) == 0) {
  cat("No potential protocol deviations or violations were detected by the configured checks.\n")
} else {
  summary_table <- protocol_summary |>
    rename(
      Classification = classification,
      `Automated screening flag` = issue,
      Participants = participants,
      `Flagged records` = flagged_records
    ) |>
    kable(format = "html", align = c("l", "l", "r", "r"))
  cat('<div class="monitor-table-scroll protocol-summary-table">', summary_table, '</div>', sep = "\n")
}
```

The participant-level review file is regenerated on every render as `protocol_deviation_violation_review.csv`. In production, it remains in the protected project folder and is not copied into the publishable `docs/` site unless publication of action lists has been explicitly enabled.

```{r}
#| label: protocol-monitoring-preview
#| results: asis

if (publish_action_lists && nrow(protocol_review) > 0) {
  protocol_preview <- protocol_review |>
    slice_head(n = config$monitoring$action_list_preview_rows) |>
    transmute(
      `Participant ID` = participant_id,
      Classification = classification,
      Issue = issue,
      Form = source_form,
      Date = record_date,
      Site = site,
      Status = review_status
    ) |>
    kable(format = "html", align = c("l", "l", "l", "l", "l", "l", "l"))
  cat('<div class="monitor-table-scroll">', protocol_preview, '</div>', sep = "\n")
} else if (!publish_action_lists && nrow(protocol_review) > 0) {
  cat("Participant-level details are hidden from the rendered production site. Use the protected review CSV for follow-up.\n")
}
```

## Recruitment funnel

**What it shows.** Unique people at successive stages from screening through daily reporting and completion of the observation window.

**How it is calculated.** A person appears in every stage they have reached, so this is a cumulative funnel rather than a set of mutually exclusive groups.

**Why it helps.** The largest drop between adjacent stages identifies where recruitment or onboarding may need attention.

```{r}
#| label: recruitment-funnel
#| fig-height: 4.5
#| fig-width: 10

funnel <- tibble(
  stage = factor(
    c("Screened", "Eligible", "Enrolled", "Submitted ≥1 daily form", followup_complete_label),
    levels = rev(c("Screened", "Eligible", "Enrolled", "Submitted ≥1 daily form", followup_complete_label))
  ),
  participants = c(
    n_screened, n_eligible, n_enrolled,
    sum(progress$daily_reports_received > 0), n_reached_followup
  )
) |>
  mutate(percent_screened = participants / n_screened)

ggplot(funnel, aes(participants, stage)) +
  geom_col(fill = "#167c77", width = .66) +
  geom_text(
    aes(label = sprintf("%s  (%s)", comma(participants), percent(percent_screened, accuracy = .1))),
    hjust = -.08, size = 3.7
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, .25))) +
  labs(x = "Participants", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

## Enrolment against site targets

**What it shows.** Enrolment achieved at each site relative to its configured target.

**How it is calculated.** Enrolled participants are counted once at their enrolment site and divided by that site's target in `dashboard_config.yml`.

**Why it helps.** It distinguishes overall recruitment success from site-specific delivery. It does not measure reporting quality after enrolment.

```{r}
#| label: site-enrolment-targets
#| fig-height: 4.2
#| fig-width: 9

site_progress <- enrolment |>
  count(organization, site, name = "enrolled") |>
  mutate(
    target = as.integer(site_targets[organization]),
    target_completion = enrolled / target
  )

ggplot(site_progress, aes(target_completion, site)) +
  geom_vline(xintercept = 1, colour = "#8c4f7d", linewidth = .7) +
  geom_col(fill = "#167c77", width = .58) +
  geom_text(
    aes(label = sprintf("%s / %s  (%s)", enrolled, target, percent(target_completion, accuracy = 1))),
    hjust = -.08, size = 3.7
  ) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, .25))) +
  labs(x = "Enrolment target reached", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

## Participant progress

**What it shows.** The current follow-up status of enrolled participants within each site.

**How it is calculated.** Status uses the configured observation window and method-discontinuation responses. “`r followup_complete_label`” means the time window elapsed; it does not require perfect questionnaire completion.

**Why it helps.** It separates participants who remain under active follow-up from those who have completed, stopped, or never begun daily reporting.

```{r}
#| label: participant-status
#| fig-height: 4.5
#| fig-width: 10

status_levels <- c(
  "Active follow-up", followup_complete_label, "Enrolled — no daily report",
  "Stopped method / follow-up ended"
)

status_by_site <- progress |>
  count(site, status) |>
  complete(site, status = status_levels, fill = list(n = 0L)) |>
  group_by(site) |>
  mutate(percent = n / sum(n), status = factor(status, levels = status_levels)) |>
  ungroup()

ggplot(status_by_site, aes(percent, site, fill = status)) +
  geom_col(width = .62) +
  geom_text(
    aes(label = if_else(percent >= .07, paste0(n, "\n", percent(percent, accuracy = 1)), "")),
    position = position_stack(vjust = .5), size = 3, lineheight = .9
  ) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = 0)) +
  scale_fill_manual(values = c("#167c77", "#8fc5c1", "#d8c8a5", "#8c4f7d")) +
  labs(x = "Percent of enrolled participants", y = NULL, fill = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
```

## Daily reporting over calendar time

**What it shows.** The proportion of expected daily reports actually received in each site-week.

**How it is calculated.** Each point divides received participant-days by expected participant-days among people under observation that week.

**Why it helps.** It separates growth in the enrolled cohort from genuine reporting adherence and makes site-specific implementation changes visible over time.

```{r}
#| label: weekly-daily-completion
#| fig-height: 5
#| fig-width: 10

due_calendar <- progress |>
  select(uniqueid, site, enrollment_date, observation_end_date) |>
  pmap_dfr(function(uniqueid, site, enrollment_date, observation_end_date) {
    tibble(uniqueid = uniqueid, site = site, date = seq(enrollment_date, observation_end_date, by = "day"))
  }) |>
  mutate(
    received = paste0(uniqueid, date) %in% paste0(cimc$uniqueid, cimc$date),
    week = as.Date(cut(date, "week", start.on.monday = TRUE))
  ) |>
  group_by(site, week) |>
  summarise(expected = n(), received = sum(received), completion = received / expected, .groups = "drop")

ggplot(due_calendar, aes(week, completion, colour = site, linetype = site)) +
  geom_line(linewidth = .8) +
  geom_point(size = 1.8) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(x = NULL, y = "Daily reports received / expected", colour = NULL, linetype = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

## Completion-pattern UpSet chart

**What it shows.** Exact combinations of reporting and follow-up milestones reached by participants.

**How it is calculated.** The upper bars count participants in each combination; filled dots identify the milestones included in that combination.

**Why it helps.** It shows whether apparent progress is driven by complete follow-up, strong daily adherence, monthly completion, or only one of those elements.

```{r}
#| label: completion-upset
#| fig-height: 7
#| fig-width: 11

completion_sets <- progress |>
  transmute(
    participant_id = uniqueid,
    `Started daily reporting` = daily_reports_received > 0,
    `At least 80% daily` = daily_completion >= config$monitoring$good_daily_completion_threshold,
    `All due monthly` = expected_monthly_reports > 0 & monthly_reports_received >= expected_monthly_reports,
    !!followup_complete_label := planned_end_date <= data_cutoff
  )

set_columns <- setdiff(names(completion_sets), "participant_id")
intersection_counts <- completion_sets |>
  count(across(all_of(set_columns)), name = "participants") |>
  arrange(desc(participants)) |>
  slice_head(n = config$display$upset_max_intersections) |>
  mutate(intersection_id = row_number())

matrix_data <- intersection_counts |>
  pivot_longer(all_of(set_columns), names_to = "milestone", values_to = "included") |>
  mutate(
    milestone = factor(milestone, levels = rev(set_columns)),
    milestone_number = as.numeric(milestone)
  )

connection_data <- matrix_data |>
  filter(included) |>
  group_by(intersection_id) |>
  summarise(ymin = min(milestone_number), ymax = max(milestone_number), .groups = "drop")

upset_bars <- ggplot(intersection_counts, aes(intersection_id, participants)) +
  geom_col(fill = "#167c77", width = .68) +
  geom_text(aes(label = participants), vjust = -.3, size = 3.3) +
  scale_x_continuous(breaks = intersection_counts$intersection_id, labels = NULL) +
  scale_y_continuous(expand = expansion(mult = c(0, .14))) +
  labs(x = NULL, y = "Participants") +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank())

upset_matrix <- ggplot(matrix_data, aes(intersection_id, milestone_number)) +
  geom_segment(
    data = connection_data,
    aes(x = intersection_id, xend = intersection_id, y = ymin, yend = ymax),
    inherit.aes = FALSE, colour = "#455553", linewidth = .6
  ) +
  geom_point(colour = "#d5dddc", size = 3) +
  geom_point(data = filter(matrix_data, included), colour = "#167c77", size = 3.5) +
  scale_x_continuous(breaks = intersection_counts$intersection_id) +
  scale_y_continuous(
    breaks = seq_along(levels(matrix_data$milestone)),
    labels = levels(matrix_data$milestone)
  ) +
  labs(x = "Exact completion-pattern intersection", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid = element_blank())

upset_bars / upset_matrix + plot_layout(heights = c(1.7, 1))
```

## Action lists

**What they contain.** Participant-level lists for specific follow-up actions, plus a complete operational progress file.

**How they are produced.** The CSVs are rebuilt from the current data every time the dashboard renders using the configured thresholds.

**Why they help.** They turn dashboard signals into practical worklists. They contain operational identifiers and dummy contact details here; production access should follow the study's role-based confidentiality controls.

```{r}
#| label: action-downloads
#| results: asis

download_card <- function(title, count, file, detail) {
  action <- if (publish_action_lists) {
    tags$a(href = file, download = file, "Download CSV")
  } else {
    tags$div(
      class = "small text-muted",
      "Generated locally; publication is disabled for production data."
    )
  }
  tags$div(
    class = "monitor-download",
    tags$strong(paste0(title, " — ", count)),
    tags$div(class = "small text-muted", detail),
    action
  )
}

downloads <- tags$div(
  class = "monitor-downloads",
  download_card(
    "Consecutive missed daily reports", nrow(reminder_targets),
    "reminder_targets_3_consecutive_missed_days.csv",
    paste0("Active participants missing at least ", missed_days_threshold, " consecutive due days")
  ),
  download_card(
    "Eligible but not enrolled", nrow(eligible_not_enrolled),
    "eligible_not_enrolled_targets.csv",
    paste0("Eligible for at least ", config$monitoring$eligible_not_enrolled_after_days, " days without an enrolment record")
  ),
  download_card(
    "Enrolled with no daily report", nrow(no_daily_targets),
    "enrolled_no_daily_submission_targets.csv",
    "Enrolled participants who have not started daily reporting"
  ),
  download_card(
    "Overdue monthly sections", nrow(monthly_due_targets),
    "monthly_report_due_targets.csv",
    "Calendar-month sections still missing after the configured grace period"
  ),
  download_card(
    "Protocol deviation/violation review", nrow(protocol_review),
    "protocol_deviation_violation_review.csv",
    "Automated cross-form flags requiring study-team verification and adjudication"
  ),
  download_card(
    "Full participant progress", nrow(progress),
    "participant_progress_summary.csv",
    "One operational progress row per enrolled participant"
  )
)

cat("```{=html}\n", as.character(downloads), "\n```\n", sep = "")
```

### Current consecutive-miss reminder list

```{r}
#| label: reminder-target-preview
#| results: asis

preview_table <- reminder_targets |>
  slice_head(n = config$monitoring$action_list_preview_rows) |>
  transmute(
    `Participant ID` = participant_id,
    Site = site,
    `Missed days` = current_consecutive_missed_days,
    `Last report` = last_report_date,
    `Reminder method` = reminder_method,
    Contact = reminder_contact,
    `Daily completion` = percent(daily_completion, accuracy = .1)
  ) |>
  kable(format = "html", align = c("l", "l", "r", "l", "l", "l", "r"))

cat('<div class="monitor-table-scroll">', preview_table, '</div>', sep = "\n")
```

## Monitoring definitions

- **Expected daily reports** run from enrolment through the earliest of the configured follow-up day (`r expected_study_days`), the data cutoff, or a recorded method stop date.
- **Monthly reports expected** are calendar-month sections due on configured day `r monthly_due_day` of a month within that observed interval. The supplied setting matches the revised CIMC form.
- **Current consecutive missed days** count backwards from the participant's latest due day. A submitted form breaks the streak.
- **`r followup_complete_label`** describes elapsed follow-up time, not questionnaire adherence.
- All thresholds and site targets are editable in `dashboard_config.yml`.
