---
title: "Daily bleeding and pain"
subtitle: "Daily ePRO results and inferred-cycle timing"
format:
  html:
    page-layout: full
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show R code"
execute:
  echo: false
  warning: false
  message: false
---

{{< include _epro_shared.qmd >}}

## How to read this report

This report answers several related—but different—questions. Keeping the unit and denominator clear is essential because the same participant can submit many daily forms, several monthly forms, and observations from multiple menstrual cycles.

| Result type | What one observation represents | Main question answered |
|---|---|---|
| Daily summaries | One submitted daily form | What proportion of submitted days had this response? |
| Monthly summaries | One submitted participant-month | What proportion of reported months had this response? |
| Ever-reported body maps | One participant counted at most once per region | What proportion of participants reported this location at least once? |
| Cycle-specific body maps | One participant counted at most once per region and inferred cycle | Among participants reaching this cycle, who reported this location at least once? |
| Cycle-day heatmap | One participant per region, cycle, and observed cycle day | On which inferred cycle days was each pain location reported? |

**Confidence intervals.** Whiskers on proportion bar charts are participant-clustered 95% bootstrap confidence intervals. The bootstrap resamples whole participants—not individual rows—so all daily or monthly records from the same person remain together. Wider intervals mean the estimate is less precise. They describe sampling uncertainty in this dataset; they do not correct bias from missing reports, an unrepresentative sample, or a misspecified cycle rule.

**Important interpretation boundary.** These analyses are descriptive. A difference over time or between cycles is not, by itself, evidence that the contraceptive caused the difference. Formal causal questions would require a prespecified comparison design and statistical model.

## Overview

Daily percentages use submitted daily records as the denominator. Monthly percentages use submitted participant-month records. Conditional questions use only records for which the XLSForm skip logic makes the question relevant.

```{r}
#| label: summary
#| results: asis

summary_html <- tags$div(
  class = "bodymap-summary",
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Participants represented"),
    tags$div(class = "bodymap-stat-value", comma(n_participants))
  ),
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Daily submissions"),
    tags$div(class = "bodymap-stat-value", comma(n_daily_submissions))
  ),
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Monthly submissions"),
    tags$div(class = "bodymap-stat-value", comma(n_monthly_submissions))
  ),
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Median daily completion"),
    tags$div(class = "bodymap-stat-value", percent(median_daily_completion, accuracy = 0.1))
  )
)

cat("```{=html}\n", as.character(summary_html), "\n```\n", sep = "")
```

All input paths, source-field names, study-site labels, body-map limits, cycle-inference rules, and display ranges are read from `dashboard_config.yml`. Changing the configuration and rerendering the book updates every page without editing the analysis code.

## Daily questionnaire overview

The daily form records symptoms about the previous day. The dummy data contain repeated submissions from the same participants, so percentages below describe submissions rather than unique people unless stated otherwise.

**What.** This section describes bleeding and pain one day at a time.

**How.** Each submitted daily form is initially one observation. Conditional follow-up questions use only forms for which the question applied—for example, pain severity is calculated only among forms reporting pain.

**Why.** Daily reporting captures short-term variation that a monthly recall question may smooth over or forget. It is especially useful for identifying timing and symptom co-occurrence.

## Daily symptom trend

**What it shows.** The lines show the percentage of submitted daily forms reporting bleeding or pain on each calendar date.

**How to read it.** Peaks indicate dates on which a larger share of available submissions were positive. They do not necessarily mean more participants were enrolled on those dates, so completion volume and missingness should be checked alongside the trend.

```{r}
#| label: daily-trend
#| fig-height: 4.8
#| fig-width: 10

daily_trend <- daily_data |>
  group_by(report_date) |>
  summarise(
    Bleeding = mean(menstrual_bleeding_yesterday == 1, na.rm = TRUE),
    Pain = mean(menstrual_pain_yesterday == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  pivot_longer(c(Bleeding, Pain), names_to = "Symptom", values_to = "percent")

ggplot(daily_trend, aes(report_date, percent, colour = Symptom, linetype = Symptom)) +
  geom_line(linewidth = .8) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_colour_manual(values = c(Bleeding = "#167c77", Pain = "#8c4f7d")) +
  labs(x = NULL, y = "Percent of daily submissions", colour = NULL, linetype = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

### Daily symptom prevalence by study site

**What it shows.** This selected site breakdown compares the proportion of daily submissions reporting bleeding or pain across the three study sites.

**How it is calculated.** The denominator is submitted daily forms within each site. Confidence intervals resample whole participants within that site, so repeated forms from one participant remain together.

**Why it helps.** A pooled percentage can conceal operational, population, or reporting differences between sites. The chart is descriptive and should prompt investigation rather than a causal conclusion about site.

```{r}
#| label: daily-site-symptom-prevalence
#| fig-height: 4.8
#| fig-width: 11

if (isTRUE(config$site_breakdowns$daily_symptom_prevalence)) {
  daily_site_results <- bind_rows(
    summarise_response_by_site(report_data, "bleeding", "Bleeding yesterday"),
    summarise_response_by_site(report_data, "pain", "Pain yesterday")
  ) |>
    filter(
      (question == "Bleeding yesterday" & response == "Bleeding") |
        (question == "Pain yesterday" & response == "Pain")
    ) |>
    mutate(site = factor(site, levels = unname(site_labels)))

  print(
    ggplot(daily_site_results, aes(percent, site, fill = question)) +
      geom_col(position = position_dodge(width = .72), width = .62) +
      geom_errorbar(
        aes(xmin = ci_low, xmax = ci_high),
        orientation = "y",
        position = position_dodge(width = .72),
        height = .18,
        linewidth = .5
      ) +
      geom_text(
        aes(label = percent(percent, accuracy = .1)),
        position = position_dodge(width = .72),
        hjust = -.12,
        vjust = -.8,
        size = 3.2
      ) +
      scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, .18))) +
      scale_fill_manual(values = c("Bleeding yesterday" = "#167c77", "Pain yesterday" = "#8c4f7d")) +
      labs(x = "Percent of daily submissions", y = NULL, fill = NULL,
           caption = "Whiskers are participant-clustered 95% confidence intervals within site.") +
      theme_minimal(base_size = 12) +
      theme(legend.position = "top", panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
  )
}
```

## Daily menstrual bleeding

**What it shows.** Four separate distributions describe whether bleeding occurred, whether it was expected, its amount, and how that amount compared with expectation.

**How it is calculated.** Each panel has its own relevant denominator. The first two use all daily submissions; amount uses bleeding-positive submissions; comparison with expectation uses bleeding-positive submissions for which bleeding was expected.

**Why it matters.** Separating occurrence, amount, and predictability distinguishes a common but expected pattern from bleeding that is surprising or difficult to anticipate.

```{r}
#| label: bleeding-summary
#| fig-height: 5.8
#| fig-width: 12

bleeding_plot_data <- bind_rows(
  summarise_response(report_data, "bleeding", "Bleeding yesterday"),
  summarise_response(report_data, "bleeding_expected", "Expected bleeding"),
  summarise_response(
    filter(report_data, menstrual_bleeding_yesterday == 1),
    "bleeding_amount",
    "Amount among bleeding reporters"
  ),
  summarise_response(
    filter(
      report_data,
      menstrual_bleeding_yesterday == 1,
      bleeding_expected_yesterday == 2
    ),
    "bleeding_amount_expected",
    "Amount compared with expectation"
  )
) |>
  mutate(
    question = factor(
      question,
      levels = c(
        "Bleeding yesterday",
        "Expected bleeding",
        "Amount among bleeding reporters",
        "Amount compared with expectation"
      )
    )
  ) |>
  arrange(question, response_order)

plot_daily_compositions(
  bleeding_plot_data,
  question_levels = c(
    "Bleeding yesterday",
    "Expected bleeding",
    "Amount among bleeding reporters",
    "Amount compared with expectation"
  ),
  caption = paste(
    "Each row uses its own relevant denominator and sums to 100%.",
    "Participant-clustered 95% confidence intervals are listed below."
  )
)
```

```{r}
#| label: daily-bleeding-ci-table

bleeding_plot_data |>
  transmute(
    Question = as.character(question),
    Response = response,
    `Daily submissions` = participants,
    `Estimate (95% CI)` = sprintf(
      "%s (%s to %s)",
      scales::percent(percent, accuracy = .1),
      scales::percent(ci_low, accuracy = .1),
      scales::percent(ci_high, accuracy = .1)
    )
  ) |>
  kable(align = c("l", "l", "r", "r"))
```

## Daily menstrual pain

**What it shows.** These panels separate pain occurrence, expectation, severity, severity relative to expectation, and duration.

**How it is calculated.** Occurrence and expectedness use all daily submissions. Severity and duration use pain-positive submissions. Severity compared with expectation uses the subset for which pain was expected.

**Why it matters.** Frequency alone does not capture symptom burden. Severity, duration, and unexpected pain may be more relevant to acceptability and daily functioning.

```{r}
#| label: pain-summary
#| fig-height: 7
#| fig-width: 12

pain_plot_data <- bind_rows(
  summarise_response(report_data, "pain", "Pain yesterday"),
  summarise_response(report_data, "pain_expected", "Expected pain"),
  summarise_response(
    filter(report_data, menstrual_pain_yesterday == 1),
    "pain_amount",
    "Severity among pain reporters"
  ),
  summarise_response(
    filter(
      report_data,
      menstrual_pain_yesterday == 1,
      pain_expected_yesterday == 2
    ),
    "pain_amount_expected",
    "Severity compared with expectation"
  ),
  summarise_response(
    filter(report_data, menstrual_pain_yesterday == 1),
    "pain_duration",
    "Duration among pain reporters"
  )
) |>
  mutate(
    question = factor(
      question,
      levels = c(
        "Pain yesterday",
        "Expected pain",
        "Severity among pain reporters",
        "Severity compared with expectation",
        "Duration among pain reporters"
      )
    )
  ) |>
  arrange(question, response_order)

plot_daily_compositions(
  pain_plot_data,
  question_levels = c(
    "Pain yesterday",
    "Expected pain",
    "Severity among pain reporters",
    "Severity compared with expectation",
    "Duration among pain reporters"
  ),
  caption = paste(
    "Each row uses its own relevant denominator and sums to 100%.",
    "Participant-clustered 95% confidence intervals are listed below."
  )
)
```

```{r}
#| label: daily-pain-ci-table

pain_plot_data |>
  transmute(
    Question = as.character(question),
    Response = response,
    `Daily submissions` = participants,
    `Estimate (95% CI)` = sprintf(
      "%s (%s to %s)",
      scales::percent(percent, accuracy = .1),
      scales::percent(ci_low, accuracy = .1),
      scales::percent(ci_high, accuracy = .1)
    )
  ) |>
  kable(align = c("l", "l", "r", "r"))
```

## Daily bleeding and pain together

**What it shows.** Each horizontal bar is all daily submissions in one bleeding group. The two sections show the complementary proportions reporting no pain and pain, so every submitted day is represented.

**How it is calculated.** Percentages sum to 100% separately within bleeding and non-bleeding submissions. Counts are daily forms rather than unique participants; participant-clustered confidence intervals are provided below.

**Why it matters.** This is an internal descriptive comparator: it indicates whether pain is concentrated on days with bleeding. The clustered interval keeps each participant's repeated records together, but the chart still does not establish causation.

```{r}
#| label: bleeding-pain
#| fig-height: 3.8
#| fig-width: 10

bleeding_pain <- bind_rows(lapply(
  levels(report_data$bleeding),
  function(bleeding_status) {
    relevant_data <- report_data |>
      filter(bleeding == bleeding_status)
    summarise_response(relevant_data, "pain", bleeding_status) |>
      transmute(
        bleeding = bleeding_status,
        response,
        response_order,
        submissions = participants,
        denominator,
        percent,
        ci_low,
        ci_high
      )
  }
)) |>
  mutate(
    bleeding = factor(
      bleeding,
      levels = rev(levels(report_data$bleeding))
    ),
    response = factor(response, levels = c("No pain", "Pain"))
  )

ggplot(bleeding_pain, aes(percent, bleeding, fill = response)) +
  geom_col(width = .62, position = position_stack(reverse = TRUE)) +
  geom_text(
    aes(
      colour = response,
      label = sprintf(
        "%s\nn=%s · %s",
        response,
        submissions,
        scales::percent(percent, accuracy = .1)
      )
    ),
    position = position_stack(vjust = .5, reverse = TRUE),
    size = 3.3,
    lineheight = .9
  ) +
  scale_fill_manual(
    values = c("No pain" = "#dce5e3", "Pain" = "#8c4f7d"),
    guide = "none"
  ) +
  scale_colour_manual(
    values = c("No pain" = "#1f2524", "Pain" = "#ffffff"),
    guide = "none"
  ) +
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    limits = c(0, 1),
    breaks = seq(0, 1, by = .25),
    expand = expansion(mult = 0)
  ) +
  labs(
    x = "Percent within bleeding group",
    y = NULL,
    caption = "Each row sums to 100%. Participant-clustered 95% confidence intervals are listed below."
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.caption = element_text(hjust = 0),
    plot.margin = margin(8, 14, 8, 8)
  )
```

```{r}
#| label: bleeding-pain-ci-table

bleeding_pain |>
  transmute(
    `Bleeding group` = as.character(bleeding),
    `Pain response` = as.character(response),
    `Daily submissions` = submissions,
    `Estimate (95% CI)` = sprintf(
      "%s (%s to %s)",
      scales::percent(percent, accuracy = .1),
      scales::percent(ci_low, accuracy = .1),
      scales::percent(ci_high, accuracy = .1)
    )
  ) |>
  arrange(`Bleeding group`, `Pain response`) |>
  kable(align = c("l", "l", "r", "r"))
```

## Ever-reported pain location map (symmetric regions)

Locations are read only from daily submissions where `${menstrual_pain_yesterday} = '1'`, because that is when the body-map question is shown. The denominator is nevertheless all unique participants in the dataset, making each percentage the proportion of the full cohort who reported pain in that region at least once. Left and right members of an otherwise identical region pair are combined. Hands and feet also ignore dorsal/ventral surface. Arms are grouped as fore, mid, or upper; legs are grouped as lower or upper. Each participant contributes at most once to a combined region across all pain-positive daily submissions.

**What it answers.** “Did this participant ever report pain in this broader body area, regardless of side?”

**Why use it.** The symmetric view is easier to communicate and less affected by inconsistent side selection. It should be presented alongside—not instead of—the detailed map when laterality could matter.

```{r}
#| label: body-map
#| results: asis

map_html <- tags$div(
  id = "bodymap-report-symmetric",
  class = "bodymap-report",
  tags$div(
    class = "bodymap-frame",
    HTML(bodymap$markup),
    tags$div(
      class = "tooltip bodymap-hover",
      role = "status",
      `aria-live` = "polite",
      tags$div(class = "tooltip-inner")
    )
  ),
  tags$div(
    class = "bodymap-legend",
    `aria-label` = "Colour scale: percent of all participants",
    tags$div(class = "bodymap-gradient"),
    tags$div(
      class = "bodymap-legend-labels",
      tags$span("0%"),
      tags$span("Percent of all participants"),
      tags$span(sprintf("%.1f%%", bodymap$maximum))
    )
  ),
  tags$div(
    class = "bodymap-note",
    "Hover over or focus any combined limb component to see its participant count and percentage."
  ),
  tags$script(HTML("(function () {
    function initialiseBodymaps() {
      document.querySelectorAll('.bodymap-report').forEach(function (root) {
      if (root.dataset.bodymapInitialised === 'true') return;
      root.dataset.bodymapInitialised = 'true';

    const frame = root.querySelector('.bodymap-frame');
    const tooltip = root.querySelector('.bodymap-hover');
    const tooltipInner = tooltip.querySelector('.tooltip-inner');

    function regionFrom(target) {
      return target && target.closest
        ? target.closest('[data-bodymap-tooltip]')
        : null;
    }

    function showTooltip(region) {
      if (!region || !frame.contains(region)) return;
      tooltipInner.textContent = region.getAttribute('data-bodymap-tooltip');
      tooltip.classList.add('is-visible');

      const regionBox = region.getBoundingClientRect();
      const frameBox = frame.getBoundingClientRect();
      const tooltipBox = tooltip.getBoundingClientRect();
      const inset = 8;

      let left = regionBox.left - frameBox.left + regionBox.width / 2 - tooltipBox.width / 2;
      left = Math.max(inset, Math.min(left, frameBox.width - tooltipBox.width - inset));

      let top = regionBox.top - frameBox.top - tooltipBox.height - inset;
      if (top < inset) top = regionBox.bottom - frameBox.top + inset;

      tooltip.style.left = left + 'px';
      tooltip.style.top = top + 'px';
    }

    function hideTooltip() {
      tooltip.classList.remove('is-visible');
    }

    root.addEventListener('pointerover', function (event) {
      const region = regionFrom(event.target);
      if (region) showTooltip(region);
    });

    root.addEventListener('pointerout', function (event) {
      const region = regionFrom(event.target);
      const nextRegion = regionFrom(event.relatedTarget);
      if (region && nextRegion !== region) hideTooltip();
    });

    root.addEventListener('focusin', function (event) {
      const region = regionFrom(event.target);
      if (region) showTooltip(region);
    });

    root.addEventListener('focusout', hideTooltip);
      });
    }

    if (document.readyState === 'loading') {
      document.addEventListener('DOMContentLoaded', initialiseBodymaps, { once: true });
    } else {
      initialiseBodymaps();
    }
  })();"))
)

cat("```{=html}\n", as.character(map_html), "\n```\n", sep = "")

if (length(bodymap$unknown) > 0) {
  warning_html <- tags$div(
    class = "bodymap-warning",
    tags$strong("Unmatched response codes: "),
    paste(bodymap$unknown, collapse = ", ")
  )
  cat("```{=html}\n", as.character(warning_html), "\n```\n", sep = "")
}
```

### Most frequently ever-reported pain regions

```{r}
#| label: results-table
#| results: asis

region_results_for_table <- if (is.null(top_n)) {
  region_results
} else {
  slice_head(region_results, n = top_n)
}

pain_regions_table <- region_results_for_table |>
  transmute(
    Region = str_replace_all(region, "_", " "),
    `Reporting region (n)` = participants,
    `All participants (N)` = n_participants,
    `Percent of all participants` = percent(percent / 100, accuracy = 0.1)
  ) |>
  kable(format = "html", align = c("l", "r", "r", "r"))

cat(
  '<div class="bodymap-table-scroll">',
  pain_regions_table,
  '</div>',
  sep = "\n"
)
```

The window is deliberately compact, but every region remains available by scrolling. Since participants can select multiple pain regions, the location percentages are not expected to sum to 100%.

## Time since contraceptive initiation

Elapsed time since `programme_start_date` is directly observed and does not depend on bleeding-pattern inference. The chart divides follow-up into consecutive `r programme_period_days`-day programme periods. Within each period, each participant contributes once to each symptom percentage regardless of how many daily forms they submitted.

**Why this view is useful.** It asks whether the proportion of participants ever reporting bleeding or pain changes as exposure time accumulates, without requiring a menstrual cycle to be successfully inferred.

```{r}
#| label: programme-time
#| fig-height: 5
#| fig-width: 10

programme_period_results <- daily_data |>
  mutate(programme_period = days_since_contraceptive_start %/% programme_period_days + 1L) |>
  filter(between(programme_period, 1, programme_months_to_display)) |>
  group_by(participant_id, programme_period) |>
  summarise(
    Bleeding = any(menstrual_bleeding_yesterday == 1, na.rm = TRUE),
    Pain = any(menstrual_pain_yesterday == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  pivot_longer(c(Bleeding, Pain), names_to = "Symptom", values_to = "reported") |>
  group_by(programme_period, Symptom) |>
  summarise(
    participants = n(),
    reporting = sum(reported),
    percent = reporting / participants,
    .groups = "drop"
  ) |>
  mutate(
    ci_z = qnorm(1 - (1 - confidence_level) / 2),
    ci_centre = (percent + ci_z^2 / (2 * participants)) /
      (1 + ci_z^2 / participants),
    ci_half_width = ci_z /
      (1 + ci_z^2 / participants) *
      sqrt(percent * (1 - percent) / participants + ci_z^2 / (4 * participants^2)),
    ci_low = pmax(0, ci_centre - ci_half_width),
    ci_high = pmin(1, ci_centre + ci_half_width)
  )

ggplot(programme_period_results, aes(programme_period, percent, colour = Symptom)) +
  geom_ribbon(
    aes(ymin = ci_low, ymax = ci_high, fill = Symptom, group = Symptom),
    colour = NA,
    alpha = .18
  ) +
  geom_line(linewidth = .8) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = seq_len(programme_months_to_display)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_colour_manual(values = c(Bleeding = "#167c77", Pain = "#8c4f7d")) +
  scale_fill_manual(values = c(Bleeding = "#167c77", Pain = "#8c4f7d"), guide = "none") +
  labs(
    x = paste0(programme_period_days, "-day period since contraceptive initiation"),
    y = "Percent of participants reporting symptom",
    colour = NULL,
    caption = "Shaded ribbons are participant-level 95% Wilson confidence intervals."
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    panel.grid.minor = element_blank(),
    plot.caption = element_text(hjust = 0)
  )
```

## Inferred menstrual cycles and cycle length

Cycle numbering is participant-specific and begins after `programme_start_date`, the contraceptive/programme start date. The first confirmed menstrual onset after that date is inferred cycle 1, followed by inferred cycle 2, cycle 3, and so on. With the supplied configuration, CD1 is the first non-spotting bleeding day followed by blood reported on the next consecutive calendar day. Confirmed onsets less than the configured minimum interval apart are not allowed to increment the inferred cycle number. Distinct shorter events remain bleeding episodes and can be analysed separately.

**What is being inferred.** The form does not contain an official cycle number or confirmed biological cycle start. The analysis therefore applies an explicit, configurable rule to observed bleeding reports.

**Why this needs caution.** Missing daily forms can hide an onset and make two true cycles appear as one long interval. Long intervals are retained and flagged rather than silently removed, so the team can review whether they reflect genuine bleeding patterns or incomplete observation.

```{r}
#| label: programme-cycles-calculate

daily_cycle_flags <- daily_data |>
  filter(report_date >= programme_start_date) |>
  arrange(participant_id, report_date) |>
  group_by(participant_id) |>
  mutate(
    blood_reported = menstrual_bleeding_yesterday == 1,
    qualifying_onset_day = blood_reported &
      (spotting_starts_cycle | bleeding_amount_yesterday >= 2),
    next_calendar_day_observed = lead(report_date) == report_date + 1,
    blood_reported_next_day = next_calendar_day_observed & lead(blood_reported),
    confirmed_onset_candidate = qualifying_onset_day &
      (!require_next_day_blood | blood_reported_next_day)
  ) |>
  ungroup()

# Standard bleeding/spotting episodes are separated by the configured number
# of blood-free days. Calendar gaps larger than one day make the boundary
# uncertain, so they are not silently treated as observed blood-free days.
episode_start_flags <- daily_cycle_flags |>
  group_by(participant_id) |>
  mutate(
    first_blood_report = blood_reported & cumsum(blood_reported) == 1L,
    preceding_days_observed_and_clear = case_when(
      bleed_free_days_between_episodes == 1 ~
        lag(report_date) == report_date - 1 & !lag(blood_reported),
      bleed_free_days_between_episodes == 2 ~
        lag(report_date) == report_date - 1 &
          lag(report_date, 2) == report_date - 2 &
          !lag(blood_reported) & !lag(blood_reported, 2),
      TRUE ~ FALSE
    ),
    bleeding_episode_start = blood_reported &
      (first_blood_report | preceding_days_observed_and_clear)
  ) |>
  ungroup()

bleeding_episode_starts <- episode_start_flags |>
  filter(bleeding_episode_start) |>
  arrange(participant_id, report_date) |>
  group_by(participant_id) |>
  transmute(
    participant_id,
    programme_start_date,
    bleeding_episode_number = row_number(),
    episode_start_date = report_date
  ) |>
  ungroup()

# Select confirmed onset candidates recursively so that a short intervening
# event cannot block a later valid onset merely because it appeared in lag().
select_separated_onsets <- function(data, minimum_days) {
  if (nrow(data) == 0) return(data)
  keep <- logical(nrow(data))
  last_kept_date <- as.Date(NA)
  for (index in seq_len(nrow(data))) {
    current_date <- data$report_date[[index]]
    if (is.na(last_kept_date) || as.integer(current_date - last_kept_date) >= minimum_days) {
      keep[[index]] <- TRUE
      last_kept_date <- current_date
    }
  }
  data[keep, , drop = FALSE]
}

qualifying_bleeding_days <- daily_cycle_flags |>
  filter(confirmed_onset_candidate) |>
  arrange(participant_id, report_date) |>
  group_by(participant_id) |>
  group_modify(~ select_separated_onsets(.x, minimum_cycle_gap_days)) |>
  ungroup() |>
  transmute(
    participant_id,
    programme_start_date,
    onset_date = report_date
  ) |>
  arrange(participant_id, onset_date) |>
  group_by(participant_id) |>
  mutate(
    cycle_number = row_number(),
    next_onset_date = lead(onset_date),
    cycle_length = as.integer(next_onset_date - onset_date)
  ) |>
  ungroup()

# Each daily report is assigned to one and only one programme cycle: the most
# recent CD1, ending immediately before the next CD1.
cycle_daily <- daily_data |>
  inner_join(
    qualifying_bleeding_days,
    by = c("participant_id", "programme_start_date"),
    relationship = "many-to-many"
  ) |>
  filter(
    report_date >= onset_date,
    is.na(next_onset_date) | report_date < next_onset_date
  ) |>
  mutate(cycle_day = as.integer(report_date - onset_date) + 1)

completed_cycles <- qualifying_bleeding_days |>
  filter(!is.na(cycle_length))
```

```{r}
#| label: cycle-lengths
#| fig-height: 5.5
#| fig-width: 10

ggplot(
  filter(completed_cycles, cycle_number <= cycles_to_display) |>
    mutate(
      interval_status = if_else(
        cycle_length > long_cycle_review_days,
        paste0("> ", long_cycle_review_days, " days: review"),
        paste0("≤ ", long_cycle_review_days, " days")
      )
    ),
  aes(factor(cycle_number), cycle_length)
) +
  geom_boxplot(fill = "#b8ddda", colour = "#167c77", outlier.shape = NA) +
  geom_jitter(aes(colour = interval_status), width = .12, alpha = .6) +
  scale_colour_manual(
    values = setNames(
      c("#064743", "#c75b12"),
      c(
        paste0("≤ ", long_cycle_review_days, " days"),
        paste0("> ", long_cycle_review_days, " days: review")
      )
    )
  ) +
  labs(
    x = "Inferred cycle number since programme start",
    y = "Observed cycle length (days)",
    colour = "Interval status"
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.minor = element_blank())
```

The final observed cycle for each participant has no subsequent CD1 and is therefore right-censored; it is not included in the cycle-length chart. Intervals longer than the configurable review threshold are retained and highlighted: these may be genuine long intervals, or may indicate that an intervening onset was missed because the required daily reports were unavailable.

```{r}
#| label: cycle-availability

cycle_availability <- qualifying_bleeding_days |>
  filter(cycle_number <= cycles_to_display) |>
  group_by(cycle_number) |>
  summarise(
    `Participants reaching inferred cycle` = n_distinct(participant_id),
    `Participants with completed cycle` = n_distinct(participant_id[!is.na(cycle_length)]),
    .groups = "drop"
  ) |>
  rename(`Inferred cycle` = cycle_number)

kable(cycle_availability, align = c("r", "r", "r"))
```

## Ever-reported pain by inferred cycle

Within each numbered cycle, a participant contributes at most once to each body region. The denominator is participants with that observed cycle, not daily submissions.

**What it shows.** Each small bar chart asks whether a region was reported at least once during inferred cycles 1, 2, and 3.

**Why it matters.** This separates a persistent location from one that becomes more or less common over successive programme cycles. The shared percentage scale supports comparison across regions; the confidence interval reflects the number of participants reaching each cycle.

```{r}
#| label: pain-by-programme-cycle
#| fig-height: 28
#| fig-width: 12

completed_cycle_keys <- completed_cycles |>
  filter(cycle_number <= cycles_to_display) |>
  select(participant_id, cycle_number)

cycle_denominators <- completed_cycle_keys |>
  distinct(participant_id, cycle_number) |>
  count(cycle_number, name = "eligible_participants")

cycle_region_results <- cycle_daily |>
  semi_join(completed_cycle_keys, by = c("participant_id", "cycle_number")) |>
  filter(menstrual_pain_yesterday == 1) |>
  transmute(
    participant_id,
    cycle_number,
    region = str_split(coalesce(.data[[location_field]], ""), "\\s+")
  ) |>
  unnest_longer(region) |>
  filter(!is.na(region), region != "") |>
  mutate(region = combine_regions(region)) |>
  distinct(participant_id, cycle_number, region) |>
  count(cycle_number, region, name = "participants") |>
  complete(
    cycle_number = seq_len(cycles_to_display),
    region = all_symmetric_regions,
    fill = list(participants = 0L)
  ) |>
  left_join(cycle_denominators, by = "cycle_number") |>
  mutate(
    percent = participants / eligible_participants,
    ci_z = qnorm(1 - (1 - confidence_level) / 2),
    ci_centre = (percent + ci_z^2 / (2 * eligible_participants)) /
      (1 + ci_z^2 / eligible_participants),
    ci_half_width = ci_z /
      (1 + ci_z^2 / eligible_participants) *
      sqrt(
        percent * (1 - percent) / eligible_participants +
          ci_z^2 / (4 * eligible_participants^2)
      ),
    ci_low = pmax(0, ci_centre - ci_half_width),
    ci_high = pmin(1, ci_centre + ci_half_width)
  )

ggplot(
  cycle_region_results |>
    mutate(region_label = str_replace_all(region, "_", " ")),
  aes(factor(cycle_number), percent)
) +
  geom_col(fill = "#167c77", width = .72) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    width = .15,
    linewidth = .4
  ) +
  geom_text(
    aes(
      y = pmin(ci_high + .025, 1),
      label = if_else(is.na(percent), "—", scales::percent(percent, accuracy = 1))
    ),
    vjust = 0,
    size = 2.5
  ) +
  facet_wrap(
    vars(region_label),
    ncol = 3,
    axes = "all_x",
    axis.labels = "all_x"
  ) +
  scale_y_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0, .10))
  ) +
  labs(
    x = "Inferred cycle number since programme start",
    y = "Percent of participants with the observed cycle",
    caption = "Whiskers are participant-level 95% Wilson confidence intervals."
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    strip.text = element_text(face = "bold"),
    plot.margin = margin(t = 14, r = 10, b = 10, l = 10)
  )
```

Each facet shows one symmetric pain region, including regions with no reports. A zero means that participants reached that inferred cycle but nobody reported the region; a dash means that no participant had an eligible completed cycle for that cell. The table below provides the same complete results numerically.

```{r}
#| label: all-regions-by-cycle-table
#| results: asis

cycle_region_rank <- cycle_region_results |>
  group_by(region) |>
  summarise(
    aggregate_percent = sum(participants, na.rm = TRUE) /
      sum(eligible_participants, na.rm = TRUE),
    .groups = "drop"
  )

cycle_regions_table <- cycle_region_results |>
  left_join(cycle_region_rank, by = "region") |>
  transmute(
    Region = str_replace_all(region, "_", " "),
    aggregate_percent,
    cycle_number,
    value = sprintf(
      "%s (%s)",
      participants,
      percent(percent, accuracy = .1)
    )
  ) |>
  pivot_wider(
    names_from = cycle_number,
    names_prefix = "Inferred cycle ",
    values_from = value,
    values_fill = "0 (0.0%)"
  ) |>
  arrange(desc(aggregate_percent), Region) |>
  select(-aggregate_percent) |>
  kable(format = "html", align = c("l", rep("r", cycles_to_display)))

cat(
  '<div class="bodymap-table-scroll">',
  cycle_regions_table,
  '</div>',
  sep = "\n"
)
```

Regions are ordered by their aggregate prevalence across the displayed cycles (the total region reports divided by the total eligible participant-cycle observations). The compact window scrolls to retain every zero-valued region without overwhelming the page.

## Pain timing within successive inferred cycles

The heatmap retains actual cycle day rather than stretching every cycle to 28 days. Within each programme-cycle and cycle-day cell, each participant contributes at most once per region. The denominator is participants who submitted a daily report for that programme cycle and cycle day, so longer cycles and better reporters do not automatically contribute more weight to another cell.

**What it shows.** Darker cells indicate that a larger percentage of participants observed on that cycle day reported the body region.

**Why it matters.** The heatmap can reveal pain concentrated around inferred cycle onset, appearing later in the cycle, or recurring at similar times across successive cycles. It remains descriptive because cycle day is inferred from bleeding—not confirmed ovulation.

```{r}
#| label: cycle-day-timing-calculate

cycle_day_denominators <- cycle_daily |>
  filter(
    cycle_number <= cycles_to_display,
    between(cycle_day, 1, cycle_days_to_display)
  ) |>
  distinct(participant_id, cycle_number, cycle_day) |>
  count(cycle_number, cycle_day, name = "eligible_participants")

timing_regions_to_plot <- if (is.null(top_timing_region_n)) {
  all_symmetric_regions
} else {
  region_results |>
    slice_head(n = top_timing_region_n) |>
    pull(region)
}

cycle_day_regions <- cycle_daily |>
  filter(
    cycle_number <= cycles_to_display,
    between(cycle_day, 1, cycle_days_to_display),
    menstrual_pain_yesterday == 1
  ) |>
  transmute(
    participant_id,
    cycle_number,
    cycle_day,
    region = str_split(coalesce(.data[[location_field]], ""), "\\s+")
  ) |>
  unnest_longer(region) |>
  filter(!is.na(region), region != "") |>
  mutate(region = combine_regions(region)) |>
  distinct(participant_id, cycle_number, cycle_day, region) |>
  count(cycle_number, cycle_day, region, name = "participants") |>
  complete(
    cycle_number = seq_len(cycles_to_display),
    cycle_day = seq_len(cycle_days_to_display),
    region = all_symmetric_regions,
    fill = list(participants = 0L)
  ) |>
  left_join(cycle_day_denominators, by = c("cycle_number", "cycle_day")) |>
  mutate(percent = participants / eligible_participants)

timing_plot_data <- cycle_day_regions |>
  filter(region %in% timing_regions_to_plot) |>
  mutate(
    combined_cycle_day = (cycle_number - 1) * cycle_days_to_display + cycle_day,
    region_label = str_replace_all(region, "_", " "),
    region_label = factor(
      region_label,
      levels = rev(str_replace_all(timing_regions_to_plot, "_", " "))
    ),
    region_y = as.numeric(region_label)
  )

timing_region_breaks <- seq_along(levels(timing_plot_data$region_label))
timing_region_labels <- levels(timing_plot_data$region_label)

cycle_boundaries <- seq_len(cycles_to_display - 1) * cycle_days_to_display + .5
cycle_centres <- tibble(
  combined_cycle_day =
    (seq_len(cycles_to_display) - 1) * cycle_days_to_display +
      (cycle_days_to_display + 1) / 2,
  label = paste("Inferred cycle", seq_len(cycles_to_display)),
  region_y = length(timing_region_breaks) + 1.15
)

cycle_tick_days <- unique(c(1, seq(cycle_day_tick_interval, cycle_days_to_display, by = cycle_day_tick_interval)))
cycle_tick_days <- cycle_tick_days[cycle_tick_days < cycle_days_to_display]
cycle_tick_positions <- unlist(lapply(
  seq_len(cycles_to_display),
  function(cycle_number) {
    (cycle_number - 1) * cycle_days_to_display + cycle_tick_days
  }
))
cycle_tick_labels <- rep(cycle_tick_days, cycles_to_display)
```

```{r}
#| label: cycle-day-timing-heatmap
#| fig-height: 14
#| fig-width: 12

ggplot(timing_plot_data, aes(combined_cycle_day, region_y, fill = percent)) +
  geom_tile(colour = "white", linewidth = .3) +
  geom_vline(
    xintercept = cycle_boundaries,
    colour = "#263b39",
    linewidth = .8
  ) +
  geom_text(
    data = cycle_centres,
    aes(combined_cycle_day, region_y, label = label),
    inherit.aes = FALSE,
    fontface = "bold",
    size = 3.6
  ) +
  scale_x_continuous(
    breaks = cycle_tick_positions,
    labels = cycle_tick_labels,
    expand = expansion(mult = c(0, 0))
  ) +
  scale_y_continuous(
    breaks = timing_region_breaks,
    labels = timing_region_labels,
    expand = expansion(add = c(.5, 1.7))
  ) +
  scale_fill_gradient(
    low = "#f1f6f5", high = "#064743",
    labels = percent_format(accuracy = 1), na.value = "#eeeeee"
  ) +
  labs(
    x = "Cycle day within each inferred cycle",
    y = NULL,
    fill = "Participants\nreporting site"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 8),
    plot.margin = margin(t = 26, r = 10, b = 8, l = 8)
  ) +
  coord_cartesian(clip = "off")
```

All symmetric regions are shown in one continuous heatmap. Vertical lines separate successive inferred cycles and the x-axis restarts at cycle day 1 within each section. Explicit zero-report cells remain visible; pale grey means there was no eligible participant report for that inferred cycle day, so a percentage cannot be calculated. Set `bodymap.top_regions_timing` to an integer in the config only if a shorter, highest-prevalence subset is wanted.

### Cumulative pain-site burden within each inferred cycle

**What it shows.** This companion heatmap collapses the daily timing information into one value for each region and inferred cycle. A participant who reports a region on several days has a larger value than someone who reports it once.

**How it is calculated.** For each participant and completed inferred cycle, the numerator is observed daily forms on which the region was reported and the denominator is all observed daily forms in that cycle. These participant-level proportions are then averaged, giving every participant equal weight despite differences in form completion.

**Why it matters.** The ever-reported chart measures how widely a site occurs across participants. This measure instead captures persistence across days. A region can therefore have broad reach but low cumulative burden, or affect fewer participants repeatedly.

```{r}
#| label: cycle-region-cumulative-burden
#| fig-height: 12
#| fig-width: 9

participant_cycle_observed_days <- cycle_daily |>
  semi_join(completed_cycle_keys, by = c("participant_id", "cycle_number")) |>
  filter(
    cycle_number <= cycles_to_display,
    between(cycle_day, 1, cycle_days_to_display)
  ) |>
  distinct(participant_id, cycle_number, report_date) |>
  count(participant_id, cycle_number, name = "observed_days")

participant_cycle_region_days <- cycle_daily |>
  semi_join(completed_cycle_keys, by = c("participant_id", "cycle_number")) |>
  filter(
    cycle_number <= cycles_to_display,
    between(cycle_day, 1, cycle_days_to_display),
    menstrual_pain_yesterday == 1
  ) |>
  transmute(
    participant_id,
    cycle_number,
    report_date,
    region = str_split(coalesce(.data[[location_field]], ""), "\\s+")
  ) |>
  unnest_longer(region) |>
  filter(!is.na(region), region != "") |>
  mutate(region = combine_regions(region)) |>
  distinct(participant_id, cycle_number, report_date, region) |>
  count(participant_id, cycle_number, region, name = "region_days")

participant_cycle_burden <- crossing(
  participant_cycle_observed_days,
  region = all_symmetric_regions
) |>
  left_join(
    participant_cycle_region_days,
    by = c("participant_id", "cycle_number", "region")
  ) |>
  mutate(
    region_days = replace_na(region_days, 0L),
    observed_day_share = region_days / observed_days
  )

cycle_region_burden <- participant_cycle_burden |>
  group_by(cycle_number, region) |>
  summarise(
    participants = n(),
    region_days = sum(region_days),
    observed_days = sum(observed_days),
    mean_observed_day_share = mean(observed_day_share),
    .groups = "drop"
  )

burden_region_order <- cycle_region_burden |>
  group_by(region) |>
  summarise(
    aggregate_burden = weighted.mean(
      mean_observed_day_share,
      participants,
      na.rm = TRUE
    ),
    .groups = "drop"
  ) |>
  arrange(desc(aggregate_burden), region) |>
  pull(region)

burden_plot_data <- cycle_region_burden |>
  mutate(
    region_label = str_replace_all(region, "_", " "),
    region_label = factor(
      region_label,
      levels = rev(str_replace_all(burden_region_order, "_", " "))
    )
  )

ggplot(
  burden_plot_data,
  aes(factor(cycle_number), region_label, fill = mean_observed_day_share)
) +
  geom_tile(colour = "white", linewidth = .45) +
  geom_text(
    aes(label = scales::percent(mean_observed_day_share, accuracy = .1)),
    size = 2.7
  ) +
  scale_fill_gradient(
    low = "#f1f6f5",
    high = "#064743",
    labels = percent_format(accuracy = 1)
  ) +
  labs(
    x = "Inferred cycle number since programme start",
    y = NULL,
    fill = "Mean share of\nobserved days"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(face = "bold")
  )
```

Rows are ordered by cumulative burden across the displayed cycles. A value of 10%, for example, means that the average participant reported that region on 10% of their observed daily forms within that completed cycle. This is a reporting-day burden measure rather than a biological duration estimate: unsubmitted days remain unknown.

### Available participants by inferred cycle and cycle day

This retention-style chart shows the denominator behind the heatmap. Each line is an inferred cycle; its height on a given cycle day is the number of participants who supplied a daily report on that day. A falling line therefore reflects a mixture of shorter cycles and missing daily forms. It resembles an at-risk curve, but it is not a formal survival estimate because participants can miss one day and submit again later.

```{r}
#| label: cycle-day-denominators
#| fig-height: 5
#| fig-width: 10

cycle_day_availability <- cycle_day_denominators |>
  filter(
    cycle_number <= cycles_to_display,
    cycle_day <= cycle_days_to_display
  ) |>
  complete(
    cycle_number = seq_len(cycles_to_display),
    cycle_day = seq_len(cycle_days_to_display),
    fill = list(eligible_participants = 0L)
  ) |>
  mutate(cycle = paste("Inferred cycle", cycle_number))

ggplot(
  cycle_day_availability,
  aes(cycle_day, eligible_participants, colour = cycle, group = cycle)
) +
  geom_step(linewidth = .85, direction = "hv") +
  geom_point(size = 1.25, alpha = .75) +
  scale_x_continuous(
    breaks = unique(c(1, seq(cycle_day_tick_interval, cycle_days_to_display, by = cycle_day_tick_interval))),
    limits = c(1, cycle_days_to_display)
  ) +
  scale_y_continuous(
    breaks = pretty_breaks(),
    expand = expansion(mult = c(0, .08))
  ) +
  scale_colour_manual(
    values = c("#064743", "#2b8c87", "#8fc9c5")
  ) +
  labs(
    x = "Cycle day",
    y = "Participants with an observed daily report",
    colour = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    panel.grid.minor = element_blank()
  )
```

Cycle day is anchored to observed bleeding rather than biologically confirmed ovulation. Cycle lengths are not normalised: later days naturally have smaller denominators when fewer participants have cycles of that length or supplied a report on that day. Any local increase after a fall indicates renewed form submission, not participants re-entering a biological risk set.
