---
title: "Menstrual bleeding and pain ePRO results"
format:
  html:
    theme: default
    page-layout: full
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show R code"
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<style>
.bodymap-summary {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(170px, 1fr));
  gap: .8rem;
  margin: 0 0 1rem;
}

.bodymap-stat {
  padding: .85rem 1rem;
  border: 1px solid var(--bs-border-color);
  border-radius: .7rem;
  background: var(--bs-tertiary-bg);
}

.bodymap-stat-label {
  color: var(--bs-secondary-color);
  font-size: .85rem;
  margin-bottom: .15rem;
}

.bodymap-stat-value {
  font-size: 1.4rem;
  font-weight: 500;
}

.bodymap-frame {
  position: relative;
  width: 100%;
  max-width: 1180px;
  margin: 0 auto;
}

.bodymap-frame svg {
  display: block;
  width: 100%;
  height: auto;
  max-height: 78vh;
}

.bodymap-region {
  transition: filter 120ms ease, stroke-width 120ms ease;
}

.bodymap-region:hover {
  filter: brightness(.9) saturate(1.08);
  stroke: #173f40 !important;
  stroke-width: 1.5px !important;
}

.bodymap-region:focus {
  outline: none;
  filter: brightness(.9) saturate(1.08);
  stroke: #173f40 !important;
  stroke-width: 2px !important;
}

.bodymap-hover {
  display: none;
  position: absolute;
  pointer-events: none;
  z-index: 10;
  opacity: 0;
}

.bodymap-hover.is-visible {
  display: block;
  opacity: 1;
}

.bodymap-legend {
  max-width: 560px;
  margin: .8rem auto 1.5rem;
}

.bodymap-gradient {
  height: .8rem;
  border-radius: 999px;
  background: linear-gradient(90deg, #f1f6f5, #b8ddda, #61b9b2, #167c77, #064743);
}

.bodymap-legend-labels {
  display: flex;
  justify-content: space-between;
  color: var(--bs-secondary-color);
  font-size: .82rem;
  margin-top: .25rem;
}

.bodymap-note {
  color: var(--bs-secondary-color);
  text-align: center;
  margin: .35rem 0 1rem;
}

.bodymap-warning {
  border-left: 4px solid #c97a15;
  background: var(--bs-warning-bg-subtle);
  padding: .75rem 1rem;
  margin: 1rem 0;
}
</style>
```

```{r}
#| label: setup

library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(xml2)
library(htmltools)
library(scales)
library(knitr)
library(ggplot2)

# Keep these files beside this QMD, or replace them with full paths.
data_file <- "dummy_menstrual_epro_data.csv"
svg_file <- "bodymap_prototype.svg"
location_field <- "pain_locations_yesterday"

map_title <- "Menstrual pain locations — symmetric limb regions"
top_n <- 15
```

```{r}
#| label: calculate-results

stopifnot(file.exists(data_file), file.exists(svg_file))

# Find genuine bilateral pairs in the SVG. A region is combined only when both
# an exact _Left and _Right version exist; unmatched names remain separate.
svg_id_scan <- read_xml(svg_file) |>
  xml_find_all("//*[@id]") |>
  xml_attr("id")

left_bases <- svg_id_scan[str_detect(svg_id_scan, "_Left$")] |>
  str_remove("_Left$")
right_bases <- svg_id_scan[str_detect(svg_id_scan, "_Right$")] |>
  str_remove("_Right$")
paired_bases <- intersect(left_bases, right_bases)

combine_sides <- function(region) {
  base <- str_remove(region, "_(?:Left|Right)$")
  if_else(region != base & base %in% paired_bases, base, region)
}

# Hands and feet ignore both side and body surface. Arms retain their
# upper/mid/fore subdivision, and legs retain their upper/lower subdivision,
# while also ignoring side and dorsal/ventral surface.
combine_regions <- function(region) {
  side_combined <- combine_sides(region)

  case_when(
    str_detect(region, "^(?:Dorsal_Foot_Ankle|Ventral_Foot)_(?:Left|Right)$") ~ "Foot",
    str_detect(region, "^(?:Dorsal|Ventral)_Hand_(?:Left|Right)$") ~ "Hand",
    str_detect(region, "^(?:Dorsal|Ventral)_Arm_Fore_(?:Left|Right)$") ~ "Arm_Fore",
    str_detect(region, "^(?:Dorsal|Ventral)_Arm_Mid_(?:Left|Right)$") ~ "Arm_Mid",
    str_detect(region, "^(?:Dorsal|Ventral)_Arm_Upper_(?:Left|Right)$") ~ "Arm_Upper",
    str_detect(region, "^(?:Dorsal|Ventral)_Leg_Lower_(?:Left|Right)$") ~ "Leg_Lower",
    str_detect(region, "^(?:Dorsal|Ventral)_Leg_Upper_(?:Left|Right)$") ~ "Leg_Upper",
    TRUE ~ side_combined
  )
}

participant_data <- read_csv(data_file, show_col_types = FALSE)

required_fields <- c(
  "participant_id",
  "menstrual_bleeding_yesterday",
  "bleeding_expected_yesterday",
  "bleeding_amount_yesterday",
  "bleeding_amount_expected_yesterday",
  "menstrual_pain_yesterday",
  "pain_expected_yesterday",
  "pain_amount_yesterday",
  "pain_amount_expected_yesterday",
  "pain_duration_yesterday",
  location_field
)

missing_fields <- setdiff(required_fields, names(participant_data))
if (length(missing_fields) > 0) {
  stop("Missing required field(s): ", paste(missing_fields, collapse = ", "))
}

n_participants <- nrow(participant_data)
if (n_participants == 0) {
  stop("The dataset contains no participant records.")
}

report_data <- participant_data |>
  mutate(
    bleeding = factor(
      menstrual_bleeding_yesterday,
      levels = c(0, 1),
      labels = c("No bleeding", "Bleeding")
    ),
    bleeding_expected = factor(
      bleeding_expected_yesterday,
      levels = 1:3,
      labels = c(
        "Did not expect bleeding",
        "Expected bleeding",
        "Unsure whether to expect bleeding"
      )
    ),
    bleeding_amount = factor(
      bleeding_amount_yesterday,
      levels = 1:4,
      labels = c("Spotting", "Light", "Moderate", "Heavy"),
      ordered = TRUE
    ),
    bleeding_amount_expected = factor(
      bleeding_amount_expected_yesterday,
      levels = 1:4,
      labels = c(
        "Amount expected",
        "Lighter than expected",
        "Heavier than expected",
        "Unsure what amount to expect"
      )
    ),
    pain = factor(
      menstrual_pain_yesterday,
      levels = c(0, 1),
      labels = c("No pain", "Pain")
    ),
    pain_expected = factor(
      pain_expected_yesterday,
      levels = 1:3,
      labels = c(
        "Did not expect pain",
        "Expected pain",
        "Unsure whether to expect pain"
      )
    ),
    pain_amount = factor(
      pain_amount_yesterday,
      levels = 1:4,
      labels = c("Mild", "Moderate", "Severe", "Very severe"),
      ordered = TRUE
    ),
    pain_amount_expected = factor(
      pain_amount_expected_yesterday,
      levels = 1:4,
      labels = c(
        "Severity expected",
        "Less severe than expected",
        "More severe than expected",
        "Unsure what severity to expect"
      )
    ),
    pain_duration = factor(
      pain_duration_yesterday,
      levels = 1:4,
      labels = c(
        "Briefly or for a short time",
        "For part of the day",
        "All day, on and off",
        "All day, constantly"
      ),
      ordered = TRUE
    )
  )

n_bleeding <- sum(participant_data$menstrual_bleeding_yesterday == 1, na.rm = TRUE)
n_pain <- sum(participant_data$menstrual_pain_yesterday == 1, na.rm = TRUE)
n_severe_pain <- sum(participant_data$pain_amount_yesterday %in% c(3, 4), na.rm = TRUE)

summarise_response <- function(data, variable, question) {
  denominator <- nrow(data)
  data |>
    filter(!is.na(.data[[variable]])) |>
    mutate(
      response_order = as.integer(.data[[variable]]),
      response = as.character(.data[[variable]])
    ) |>
    count(response_order, response, name = "participants") |>
    mutate(
      denominator = denominator,
      percent = participants / denominator,
      question = question
    )
}

# Each row is one participant. A participant is counted at most once in each
# combined body region, even if more than one component was selected.
region_results <- participant_data |>
  transmute(
    participant_row = row_number(),
    region = str_split(coalesce(.data[[location_field]], ""), "\\s+")
  ) |>
  unnest_longer(region) |>
  filter(!is.na(region), region != "") |>
  mutate(region = combine_regions(region)) |>
  distinct(participant_row, region) |>
  count(region, name = "participants") |>
  mutate(percent = participants / n_participants * 100) |>
  arrange(desc(percent), region)

n_reporting <- n_pain
total_selections <- sum(region_results$participants)
```

```{r}
#| label: svg-functions

set_svg_fill <- function(node, colour) {
  style <- xml_attr(node, "style")
  style[is.na(style)] <- ""

  if (str_detect(style, "(^|;)\\s*fill\\s*:")) {
    style <- str_replace(
      style,
      "((^|;)\\s*fill\\s*:)\\s*[^;]+",
      paste0("\\1", colour)
    )
  } else {
    separator <- if_else(style == "", "", ";")
    style <- paste0(style, separator, "fill:", colour)
  }

  xml_set_attr(node, "style", style)
  existing_class <- xml_attr(node, "class")
  existing_class[is.na(existing_class)] <- ""
  xml_set_attr(node, "class", str_squish(paste(existing_class, "bodymap-region")))
}

build_bodymap <- function(svg_file, results, title) {
  svg <- read_xml(svg_file)
  root <- xml_root(svg)

  if (is.na(xml_attr(root, "viewBox"))) {
    width <- parse_number(xml_attr(root, "width"))
    height <- parse_number(xml_attr(root, "height"))
    xml_set_attr(root, "viewBox", paste(0, 0, width, height))
  }

  xml_set_attr(root, "width", "100%")
  xml_set_attr(root, "height", "auto")
  xml_set_attr(root, "role", "img")
  xml_set_attr(root, "aria-label", title)

  # Select only drawable body-region objects. This excludes Affinity's embedded
  # background image and definition IDs while retaining grouped regions.
  id_nodes <- xml_find_all(
    svg,
    "//*[@id and (self::*[local-name()='path' or local-name()='polygon' or local-name()='rect' or local-name()='circle' or local-name()='ellipse'] or ./*[local-name()='path' or local-name()='polygon' or local-name()='rect' or local-name()='circle' or local-name()='ellipse'])]"
  )
  svg_ids <- xml_attr(id_nodes, "id")

  mapped <- tibble(
    svg_region = svg_ids,
    region = combine_regions(svg_ids)
  ) |>
    left_join(results, by = "region") |>
    mutate(
      participants = replace_na(participants, 0L),
      percent = replace_na(percent, 0)
    )

  scale_max <- max(mapped$percent, 1)
  fill_scale <- col_numeric(
    palette = c("#f1f6f5", "#b8ddda", "#61b9b2", "#167c77", "#064743"),
    domain = c(0, scale_max),
    na.color = "#f1f6f5"
  )

  for (index in seq_len(nrow(mapped))) {
    svg_region <- mapped$svg_region[[index]]
    region <- mapped$region[[index]]
    node <- xml_find_first(svg, sprintf("//*[@id='%s']", svg_region))

    shape_nodes <- if (xml_name(node) %in% c("path", "polygon", "rect", "circle", "ellipse")) {
      xml_find_all(node, "self::*")
    } else {
      xml_find_all(
        node,
        ".//*[local-name()='path' or local-name()='polygon' or local-name()='rect' or local-name()='circle' or local-name()='ellipse']"
      )
    }

    colour <- fill_scale(mapped$percent[[index]])
    for (node_index in seq_along(shape_nodes)) {
      set_svg_fill(shape_nodes[[node_index]], colour)
    }

    old_titles <- xml_find_all(node, "./*[local-name()='title']")
    xml_remove(old_titles)
    tooltip <- sprintf(
      "%s: %d participant%s (%.1f%%)",
      str_replace_all(region, "_", " "),
      mapped$participants[[index]],
      if_else(mapped$participants[[index]] == 1, "", "s"),
      mapped$percent[[index]]
    )
    xml_set_attr(node, "data-bodymap-tooltip", tooltip)
    xml_set_attr(node, "aria-label", tooltip)
    xml_set_attr(node, "tabindex", "0")
    xml_add_child(node, "title", tooltip, .where = 1)
  }

  list(
    markup = as.character(root),
    mapped = mapped,
    unknown = setdiff(results$region, unique(combine_regions(svg_ids))),
    maximum = scale_max
  )
}

bodymap <- build_bodymap(svg_file, region_results, map_title)
```

## Overview

Percentages in the overview use all submitted participant records as the denominator. Conditional questions use only the participants for whom that question was relevant under the XLSForm skip logic.

```{r}
#| label: summary
#| results: asis

summary_html <- tags$div(
  class = "bodymap-summary",
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Participants analysed"),
    tags$div(class = "bodymap-stat-value", comma(n_participants))
  ),
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Reported bleeding"),
    tags$div(
      class = "bodymap-stat-value",
      sprintf("%s (%s)", comma(n_bleeding), percent(n_bleeding / n_participants, accuracy = 0.1))
    )
  ),
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Reported menstrual pain"),
    tags$div(
      class = "bodymap-stat-value",
      sprintf("%s (%s)", comma(n_pain), percent(n_pain / n_participants, accuracy = 0.1))
    )
  ),
  tags$div(
    class = "bodymap-stat",
    tags$div(class = "bodymap-stat-label", "Severe/very severe among pain reporters"),
    tags$div(
      class = "bodymap-stat-value",
      if (n_pain == 0) "Not estimable" else
        sprintf("%s (%s)", comma(n_severe_pain), percent(n_severe_pain / n_pain, accuracy = 0.1))
    )
  )
)

cat("```{=html}\n", as.character(summary_html), "\n```\n", sep = "")
```

## Menstrual bleeding

```{r}
#| label: bleeding-summary
#| fig-height: 9
#| fig-width: 10

bleeding_plot_data <- bind_rows(
  summarise_response(report_data, "bleeding", "Bleeding yesterday"),
  summarise_response(report_data, "bleeding_expected", "Expected bleeding"),
  summarise_response(
    filter(report_data, menstrual_bleeding_yesterday == 1),
    "bleeding_amount",
    "Amount among bleeding reporters"
  ),
  summarise_response(
    filter(
      report_data,
      menstrual_bleeding_yesterday == 1,
      bleeding_expected_yesterday == 2
    ),
    "bleeding_amount_expected",
    "Amount compared with expectation"
  )
) |>
  mutate(
    question = factor(
      question,
      levels = c(
        "Bleeding yesterday",
        "Expected bleeding",
        "Amount among bleeding reporters",
        "Amount compared with expectation"
      )
    )
  )

ggplot(bleeding_plot_data, aes(x = percent, y = reorder(response, response_order))) +
  geom_col(fill = "#167c77", width = 0.68) +
  geom_text(
    aes(label = sprintf("%s  %s", participants, percent(percent, accuracy = 0.1))),
    hjust = -0.05,
    size = 3.5
  ) +
  facet_grid(question ~ ., scales = "free_y", space = "free_y") +
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0, 0.24))
  ) +
  labs(x = "Percent within the relevant group", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.y = element_text(angle = 0, face = "bold"),
    plot.margin = margin(8, 42, 8, 8)
  )
```

## Menstrual pain

```{r}
#| label: pain-summary
#| fig-height: 11
#| fig-width: 10

pain_plot_data <- bind_rows(
  summarise_response(report_data, "pain", "Pain yesterday"),
  summarise_response(report_data, "pain_expected", "Expected pain"),
  summarise_response(
    filter(report_data, menstrual_pain_yesterday == 1),
    "pain_amount",
    "Severity among pain reporters"
  ),
  summarise_response(
    filter(
      report_data,
      menstrual_pain_yesterday == 1,
      pain_expected_yesterday == 2
    ),
    "pain_amount_expected",
    "Severity compared with expectation"
  ),
  summarise_response(
    filter(report_data, menstrual_pain_yesterday == 1),
    "pain_duration",
    "Duration among pain reporters"
  )
) |>
  mutate(
    question = factor(
      question,
      levels = c(
        "Pain yesterday",
        "Expected pain",
        "Severity among pain reporters",
        "Severity compared with expectation",
        "Duration among pain reporters"
      )
    )
  )

ggplot(pain_plot_data, aes(x = percent, y = reorder(response, response_order))) +
  geom_col(fill = "#167c77", width = 0.68) +
  geom_text(
    aes(label = sprintf("%s  %s", participants, percent(percent, accuracy = 0.1))),
    hjust = -0.05,
    size = 3.5
  ) +
  facet_grid(question ~ ., scales = "free_y", space = "free_y") +
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0, 0.24))
  ) +
  labs(x = "Percent within the relevant group", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.y = element_text(angle = 0, face = "bold"),
    plot.margin = margin(8, 42, 8, 8)
  )
```

## Bleeding and pain together

```{r}
#| label: bleeding-pain
#| fig-height: 4.5
#| fig-width: 9

bleeding_pain <- report_data |>
  group_by(bleeding) |>
  summarise(
    participants = n(),
    pain_reporters = sum(menstrual_pain_yesterday == 1, na.rm = TRUE),
    percent_with_pain = pain_reporters / participants,
    .groups = "drop"
  )

ggplot(bleeding_pain, aes(x = percent_with_pain, y = bleeding)) +
  geom_col(fill = "#167c77", width = 0.58) +
  geom_text(
    aes(label = sprintf("%s/%s  %s", pain_reporters, participants, percent(percent_with_pain, accuracy = 0.1))),
    hjust = -0.05,
    size = 3.8
  ) +
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0, 0.28))
  ) +
  labs(x = "Participants reporting menstrual pain", y = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.margin = margin(8, 52, 8, 8)
  )
```

## Pain location map

Left and right members of an otherwise identical region pair are combined. Hands and feet also ignore dorsal/ventral surface. Arms are grouped as fore, mid, or upper; legs are grouped as lower or upper. A participant selecting more than one component of a combined region contributes once to that region.

```{r}
#| label: body-map
#| results: asis

map_html <- tags$div(
  id = "bodymap-report",
  tags$div(
    class = "bodymap-frame",
    HTML(bodymap$markup),
    tags$div(
      class = "tooltip bodymap-hover",
      role = "status",
      `aria-live` = "polite",
      tags$div(class = "tooltip-inner")
    )
  ),
  tags$div(
    class = "bodymap-legend",
    `aria-label` = "Colour scale: percent of participants",
    tags$div(class = "bodymap-gradient"),
    tags$div(
      class = "bodymap-legend-labels",
      tags$span("0%"),
      tags$span("Percent of participants"),
      tags$span(sprintf("%.1f%%", bodymap$maximum))
    )
  ),
  tags$div(
    class = "bodymap-note",
    "Hover over or focus any combined limb component to see its participant count and percentage."
  ),
  tags$script(HTML("(function () {
    const root = document.getElementById('bodymap-report');
    if (!root) return;

    const frame = root.querySelector('.bodymap-frame');
    const tooltip = root.querySelector('.bodymap-hover');
    const tooltipInner = tooltip.querySelector('.tooltip-inner');

    function regionFrom(target) {
      return target && target.closest
        ? target.closest('[data-bodymap-tooltip]')
        : null;
    }

    function showTooltip(region) {
      if (!region || !frame.contains(region)) return;
      tooltipInner.textContent = region.getAttribute('data-bodymap-tooltip');
      tooltip.classList.add('is-visible');

      const regionBox = region.getBoundingClientRect();
      const frameBox = frame.getBoundingClientRect();
      const tooltipBox = tooltip.getBoundingClientRect();
      const inset = 8;

      let left = regionBox.left - frameBox.left + regionBox.width / 2 - tooltipBox.width / 2;
      left = Math.max(inset, Math.min(left, frameBox.width - tooltipBox.width - inset));

      let top = regionBox.top - frameBox.top - tooltipBox.height - inset;
      if (top < inset) top = regionBox.bottom - frameBox.top + inset;

      tooltip.style.left = left + 'px';
      tooltip.style.top = top + 'px';
    }

    function hideTooltip() {
      tooltip.classList.remove('is-visible');
    }

    root.addEventListener('pointerover', function (event) {
      const region = regionFrom(event.target);
      if (region) showTooltip(region);
    });

    root.addEventListener('pointerout', function (event) {
      const region = regionFrom(event.target);
      const nextRegion = regionFrom(event.relatedTarget);
      if (region && nextRegion !== region) hideTooltip();
    });

    root.addEventListener('focusin', function (event) {
      const region = regionFrom(event.target);
      if (region) showTooltip(region);
    });

    root.addEventListener('focusout', hideTooltip);
  })();"))
)

cat("```{=html}\n", as.character(map_html), "\n```\n", sep = "")

if (length(bodymap$unknown) > 0) {
  warning_html <- tags$div(
    class = "bodymap-warning",
    tags$strong("Unmatched response codes: "),
    paste(bodymap$unknown, collapse = ", ")
  )
  cat("```{=html}\n", as.character(warning_html), "\n```\n", sep = "")
}
```

### Most frequently selected pain regions

```{r}
#| label: results-table

region_results |>
  slice_head(n = top_n) |>
  transmute(
    Region = str_replace_all(region, "_", " "),
    Participants = participants,
    `Percent of participants` = percent(percent / 100, accuracy = 0.1)
  ) |>
  kable(align = c("l", "r", "r"))
```

Since participants can select multiple pain regions, the location percentages are not expected to sum to 100%.

## Data-quality checks

```{r}
#| label: data-quality

data_quality <- tibble(
  Check = c(
    "Duplicate participant IDs",
    "Bleeding amount present when no bleeding was reported",
    "Bleeding expectation comparison outside its skip condition",
    "Pain severity present when no pain was reported",
    "Pain duration present when no pain was reported",
    "Pain locations present when no pain was reported",
    "Pain expectation comparison outside its skip condition",
    "Unmatched body-map response codes"
  ),
  Issues = c(
    sum(duplicated(participant_data$participant_id)),
    sum(
      participant_data$menstrual_bleeding_yesterday == 0 &
        !is.na(participant_data$bleeding_amount_yesterday),
      na.rm = TRUE
    ),
    sum(
      !(participant_data$menstrual_bleeding_yesterday == 1 &
          participant_data$bleeding_expected_yesterday == 2) &
        !is.na(participant_data$bleeding_amount_expected_yesterday),
      na.rm = TRUE
    ),
    sum(
      participant_data$menstrual_pain_yesterday == 0 &
        !is.na(participant_data$pain_amount_yesterday),
      na.rm = TRUE
    ),
    sum(
      participant_data$menstrual_pain_yesterday == 0 &
        !is.na(participant_data$pain_duration_yesterday),
      na.rm = TRUE
    ),
    sum(
      participant_data$menstrual_pain_yesterday == 0 &
        !is.na(participant_data[[location_field]]) &
        str_trim(participant_data[[location_field]]) != "",
      na.rm = TRUE
    ),
    sum(
      !(participant_data$menstrual_pain_yesterday == 1 &
          participant_data$pain_expected_yesterday == 2) &
        !is.na(participant_data$pain_amount_expected_yesterday),
      na.rm = TRUE
    ),
    length(bodymap$unknown)
  )
)

kable(data_quality, align = c("l", "r"))
```

## Analysis notes

- Each row is treated as one participant submission.
- Overall bleeding and pain percentages use all submitted rows as the denominator.
- Severity, amount, duration, and comparison-with-expectation questions use only rows for which the XLSForm says the question is relevant.
- This is descriptive analysis. The report does not test causal relationships or make clinical interpretations.
