---
title: "Participant follow-up calendar"
subtitle: "Full-protocol daily and monthly completion patterns"
format:
  html:
    page-layout: full
    toc: true
    toc-depth: 2
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: followup-calendar-setup

library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(ggplot2)
library(scales)
library(knitr)
library(yaml)
library(htmltools)

config <- read_yaml("dashboard_config.yml")
id_column_type <- cols(uniqueid = col_character())
enrolment_raw <- read_csv(
  config$files$enrolment, col_types = id_column_type, show_col_types = FALSE
)
cimc <- read_csv(
  config$files$cimc, col_types = id_column_type, show_col_types = FALSE
)
refresh_metadata <- read_csv(config$files$refresh_metadata, show_col_types = FALSE)

data_mode <- tolower(config$data_source$mode)
mode_settings <- config$data_source[[data_mode]]
publish_action_lists <- isTRUE(mode_settings$publish_action_lists_in_rendered_site)
data_cutoff <- as.Date(first(refresh_metadata$effective_data_cutoff))
protocol_days <- as.integer(config$study$expected_daily_reports)
monthly_due_day <- as.integer(config$study$monthly_due_day)
site_labels <- unlist(config$labels$sites)
sort_method <- tolower(config$monitoring$full_tracking_sort)
max_participants <- config$monitoring$full_tracking_max_participants
row_height <- config$monitoring$full_tracking_row_height_inches
scroll_height <- config$display$full_tracking_scroll_height

for (field in c("_id", "organization", "enrollment_date")) {
  if (!field %in% names(enrolment_raw)) enrolment_raw[[field]] <- NA
}
for (field in c("date", "monthly_report_due", "QA", "QB")) {
  if (!field %in% names(cimc)) cimc[[field]] <- NA
}

canonical_latest_record <- function(data) {
  source_order <- seq_len(nrow(data))
  kobo_order <- suppressWarnings(as.numeric(data[["_id"]]))
  data |>
    mutate(
      uniqueid = as.character(uniqueid),
      .canonical_order = coalesce(kobo_order, as.numeric(source_order))
    ) |>
    arrange(uniqueid, desc(.canonical_order)) |>
    distinct(uniqueid, .keep_all = TRUE) |>
    select(-.canonical_order)
}

enrolment <- canonical_latest_record(enrolment_raw) |>
  mutate(
    enrollment_date = as.Date(as.character(enrollment_date)),
    site = unname(site_labels[as.character(organization)])
  ) |>
  filter(!is.na(uniqueid), !is.na(enrollment_date))

cimc <- cimc |>
  mutate(
    uniqueid = as.character(uniqueid),
    date = as.Date(as.character(date)),
    monthly_report_due = str_to_lower(as.character(monthly_report_due)),
    method_stop_date = as.Date(as.character(QB))
  )

method_stops <- cimc |>
  filter(as.character(QA) %in% c("0", "no"), !is.na(method_stop_date)) |>
  group_by(uniqueid) |>
  summarise(method_stop_date = min(method_stop_date), .groups = "drop")

participants <- enrolment |>
  left_join(method_stops, by = "uniqueid") |>
  mutate(
    planned_end_date = enrollment_date + protocol_days - 1L,
    observed_end_date = pmin(
      planned_end_date, data_cutoff, coalesce(method_stop_date, data_cutoff),
      na.rm = TRUE
    ),
    site = replace_na(as.character(site), "Site unavailable")
  )

if (protocol_days < 1L) {
  stop("study.expected_daily_reports must be at least 1.")
}

if (nrow(participants) == 0) {
  empty_gap_summary <- tibble(
    participant_id = character(), site = character(), enrollment_date = as.Date(character()),
    planned_end_date = as.Date(character()), observed_end_date = as.Date(character()),
    observed_days = integer(), daily_received = integer(), missed_days = integer(),
    gap_episodes = integer(), longest_gap = integer(), monthly_due = integer(),
    monthly_received = integer(), monthly_missed = integer(), current_completion = double()
  )
  write_csv(empty_gap_summary, "participant_followup_gap_summary.csv", na = "")
  cat(paste(
    "## Participant follow-up is not yet available\n\n",
    "No valid enrolment record is currently available. This page will populate ",
    "after an enrolled participant is staged and the dashboard is rendered again.\n"
  ))
  knitr::knit_exit()
}

daily_keys <- cimc |>
  filter(!is.na(uniqueid), !is.na(date)) |>
  distinct(uniqueid, date) |>
  transmute(key = paste(uniqueid, date)) |>
  pull(key)

monthly_keys <- cimc |>
  filter(monthly_report_due == "yes", !is.na(uniqueid), !is.na(date)) |>
  distinct(uniqueid, date) |>
  transmute(key = paste(uniqueid, date)) |>
  pull(key)

calendar_grid <- crossing(
  participants |>
    select(uniqueid, site, enrollment_date, planned_end_date, observed_end_date, method_stop_date),
  follow_up_day = seq_len(protocol_days)
) |>
  mutate(
    calendar_date = enrollment_date + follow_up_day - 1L,
    daily_received = paste(uniqueid, calendar_date) %in% daily_keys,
    monthly_received = paste(uniqueid, calendar_date) %in% monthly_keys,
    monthly_due = calendar_date <= observed_end_date &
      as.integer(format(calendar_date, "%d")) == monthly_due_day,
    due = calendar_date <= observed_end_date,
    daily_missing = due & !daily_received,
    monthly_missing = monthly_due & !monthly_received,
    result = case_when(
      !is.na(method_stop_date) & calendar_date > method_stop_date ~ "Follow-up ended",
      calendar_date > data_cutoff ~ "Future / not yet due",
      calendar_date > observed_end_date ~ "Follow-up ended",
      monthly_received ~ "Monthly + daily received",
      monthly_missing ~ "Monthly due — missing",
      daily_received ~ "Daily received",
      TRUE ~ "Daily missed"
    ),
    result = factor(
      result,
      levels = c(
        "Daily received", "Daily missed", "Monthly + daily received",
        "Monthly due — missing", "Future / not yet due", "Follow-up ended"
      )
    )
  )

gap_metrics <- calendar_grid |>
  group_by(uniqueid, site, enrollment_date, planned_end_date, observed_end_date) |>
  summarise(
    observed_days = sum(due),
    daily_received = sum(due & daily_received),
    missed_days = sum(daily_missing),
    gap_episodes = {
      runs <- rle(daily_missing[due])
      sum(runs$values)
    },
    longest_gap = {
      runs <- rle(daily_missing[due])
      if (any(runs$values)) max(runs$lengths[runs$values]) else 0L
    },
    monthly_due = sum(monthly_due),
    monthly_received = sum(monthly_due & monthly_received),
    monthly_missed = sum(monthly_missing),
    current_completion = if_else(observed_days > 0, daily_received / observed_days, NA_real_),
    .groups = "drop"
  )

valid_sort_methods <- c("gap_episodes", "missed_days", "longest_gap", "monthly_missed")
if (!sort_method %in% valid_sort_methods) {
  stop(
    "monitoring.full_tracking_sort must be one of: ",
    paste(valid_sort_methods, collapse = ", ")
  )
}

gap_metrics <- gap_metrics |>
  mutate(.sort_value = .data[[sort_method]]) |>
  arrange(desc(.sort_value), desc(longest_gap), desc(missed_days), uniqueid)

if (!is.null(max_participants)) {
  gap_metrics <- gap_metrics |> slice_head(n = as.integer(max_participants))
}

gap_metrics <- gap_metrics |>
  mutate(
    rank = row_number(),
    display_id = if (publish_action_lists) {
      uniqueid
    } else {
      paste0("Participant ", sprintf("%03d", rank))
    },
    display_label = paste0(
      display_id, "  ·  ", gap_episodes, " gap",
      if_else(gap_episodes == 1, "", "s"), " / ", missed_days, " missed"
    )
  )

calendar_display <- calendar_grid |>
  semi_join(gap_metrics, by = "uniqueid") |>
  left_join(gap_metrics |> select(uniqueid, rank, display_label), by = "uniqueid") |>
  mutate(display_label = factor(display_label, levels = rev(gap_metrics$display_label)))

write_csv(
  gap_metrics |>
    select(
      participant_id = uniqueid, site, enrollment_date, planned_end_date,
      observed_end_date, observed_days, daily_received, missed_days,
      gap_episodes, longest_gap, monthly_due, monthly_received,
      monthly_missed, current_completion
    ),
  "participant_followup_gap_summary.csv", na = ""
)

n_participants <- nrow(gap_metrics)
n_observed_days <- sum(gap_metrics$observed_days)
n_daily_received <- sum(gap_metrics$daily_received)
n_gap_episodes <- sum(gap_metrics$gap_episodes)
n_monthly_missed <- sum(gap_metrics$monthly_missed)
plot_height <- max(7, n_participants * row_height)
```

This page is the individual-level counterpart to the completion-pattern UpSet chart. It shows *where* each participant's reporting gaps occur across the full protocol period, rather than reducing their pattern to a single completion category.

**What it shows.** Each row is one participant and each column is a protocol follow-up day. Daily receipts, missed daily reports, monthly receipts, overdue monthly sections, future days, and days after early follow-up closure have distinct colours.

**How it is calculated.** Protocol day 1 is each participant's enrolment date, so participants with different calendar start dates align on the same follow-up scale. By default, rows are ordered by the number of separate missing-report episodes, then longest gap and total missed days. The ranking rule, observation duration, monthly due day, row height, and optional participant limit are all configurable.

**Why it helps.** Two participants can have the same overall completion percentage but very different operational risk: one may miss occasional isolated days while another disappears for a sustained period. This view makes those patterns visible and puts the records most likely to warrant review at the top.

```{r}
#| label: followup-calendar-kpis
#| results: asis

kpi <- function(label, value, note) {
  tags$div(
    class = "monitor-kpi",
    tags$div(class = "monitor-kpi-label", label),
    tags$div(class = "monitor-kpi-value", value),
    tags$div(class = "monitor-kpi-note", note)
  )
}

calendar_cards <- tags$div(
  class = "monitor-kpis",
  kpi("Participants displayed", comma(n_participants), paste("of", nrow(participants), "enrolled")),
  kpi("Observed participant-days", comma(n_observed_days), "Due through the data cutoff"),
  kpi("Daily completion", percent(n_daily_received / n_observed_days, accuracy = .1),
      paste(comma(n_observed_days - n_daily_received), "missed")),
  kpi("Missing-report episodes", comma(n_gap_episodes), "Separate runs of missed days"),
  kpi("Monthly sections overdue", comma(n_monthly_missed), "Due but not received")
)
cat("```{=html}\n", as.character(calendar_cards), "\n```\n", sep = "")
```

## Full protocol completion heatmap

The chart spans all `r protocol_days` configured protocol days. Vertical dividers mark each `r config$study$programme_period_days`-day programme period. Scroll vertically to review the full ordered cohort.

```{r}
#| label: followup-calendar-scroll-open
#| results: asis
cat(
  '```{=html}\n<div class="full-tracking-scroll" style="--full-tracking-height: ',
  scroll_height,
  ';">\n```\n',
  sep = ""
)
```

```{r full-tracking-heatmap, fig.height=plot_height, fig.width=14}
period_breaks <- seq(
  config$study$programme_period_days,
  protocol_days - 1L,
  by = config$study$programme_period_days
) + .5

ggplot(calendar_display, aes(follow_up_day, display_label, fill = result)) +
  geom_tile(colour = "white", linewidth = .12, width = .96, height = .86) +
  geom_vline(xintercept = period_breaks, colour = "#344b56", linewidth = .35) +
  scale_fill_manual(
    values = c(
      `Daily received` = "#59ad8b",
      `Daily missed` = "#e58d87",
      `Monthly + daily received` = "#7763a8",
      `Monthly due — missing` = "#e2ac43",
      `Future / not yet due` = "#edf1f2",
      `Follow-up ended` = "#b9c1c3"
    ),
    breaks = c(
      "Daily received", "Daily missed", "Monthly + daily received",
      "Monthly due — missing", "Future / not yet due", "Follow-up ended"
    ),
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = unique(c(1, seq(10, protocol_days, by = 10), protocol_days)),
    expand = expansion(add = .2)
  ) +
  labs(x = "Protocol follow-up day", y = NULL, fill = NULL) +
  theme_minimal(base_size = 10) +
  theme(
    legend.position = "top",
    panel.grid = element_blank(),
    axis.text.y = element_text(size = 7.5),
    plot.margin = margin(5.5, 8, 5.5, 5.5)
  )
```

```{=html}
</div>
```

## Ranked gap summary

The ranking table uses the same ordering as the heatmap. The participant-level CSV is regenerated on every render. In production it remains in the protected project directory unless action-list publication is explicitly enabled.

```{r}
#| label: followup-gap-table
#| results: asis

gap_table <- gap_metrics |>
  transmute(
    Rank = rank,
    Participant = display_id,
    Site = site,
    `Gap episodes` = gap_episodes,
    `Longest gap` = longest_gap,
    `Missed daily` = missed_days,
    `Daily completion` = percent(current_completion, accuracy = .1),
    `Monthly missed` = monthly_missed
  ) |>
  kable(format = "html", align = c("r", "l", "l", "r", "r", "r", "r", "r"))

cat('<div class="monitor-table-scroll monitor-table-compact">', gap_table, '</div>', sep = "\n")

if (publish_action_lists) {
  cat('\n[Download the ranked participant gap summary](participant_followup_gap_summary.csv){download="participant_followup_gap_summary.csv"}\n')
} else {
  cat("\nThe identified CSV is available only in the protected project output directory.\n")
}
```
