---
title: "Technical appendix"
subtitle: "Detailed ever-reported pain map"
format:
  html:
    page-layout: full
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show R code"
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: epro-data-preflight
#| results: asis

preflight_config <- yaml::read_yaml("dashboard_config.yml")
preflight_daily <- readr::read_csv(
  preflight_config$files$daily_data,
  show_col_types = FALSE
)
if (nrow(preflight_daily) == 0) {
  cat(paste(
    "## Linked ePRO results are not yet available\n\n",
    "No CIMC submission currently has both a valid participant linkage and a ",
    "programme start date. Any unlinked submissions remain visible in the ",
    "protocol-monitoring section on page 1 and in its protected review CSV. ",
    "This page will populate after a valid linked submission is received and ",
    "the dashboard is rendered again.\n"
  ))
  knitr::knit_exit()
}
```

{{< include _epro_shared.qmd >}}

## Configuring the dashboard

The dashboard's study-specific settings are held in one file: [`dashboard_config.yml`](dashboard_config.yml). This keeps choices such as study dates, site targets, reminder thresholds, cycle-inference rules, and display limits separate from the R analysis code.

**What this means.** Most routine adaptations should require a change to the configuration file followed by a fresh render—not edits scattered through the analysis pages.

**Why it helps.** Keeping assumptions in one clearly annotated file makes them easier to review with the study team, apply consistently across all pages, and record when the dashboard is updated.

### Safe editing workflow

1. Make a copy of the current `dashboard_config.yml` before making a substantial change.
2. Open the file in a plain-text editor and change only the value after the relevant colon.
3. Keep the existing indentation. YAML uses spaces to show which settings belong together; tabs should not be used.
4. Save the file, render the Quarto book again, and review the data-quality page as well as the chart affected by the change.
5. Record analytically important changes—especially cycle rules, denominators, date cutoffs, and confidence levels—so results from different dashboard versions are not compared as if their definitions were identical.

YAML values have a few conventions:

- `true` and `false` turn options on or off.
- `null` means no limit; for example, all pain regions are displayed.
- Text can be quoted, and dates should remain quoted in `YYYY-MM-DD` form.
- Proportions are written between 0 and 1, so `0.80` means 80%.
- Lists use square brackets, for example `[18, 24, 29, 34]`.

For example, this changes the missed-daily-report alert from three consecutive days to four:

```yaml
monitoring:
  consecutive_missed_days: 4
```

### Which section controls what?

| Configuration section | What to edit there | Examples of effects |
|---|---|---|
| `data_source` | Development/production mode and Kobo connection settings | Use dummy data or download current production data |
| `files` | Analysis-ready file paths | Point the R analysis to staged inputs and the body-map SVG |
| `fields` | Source column names | Adapt the dashboard if an analysis-ready variable is renamed |
| `study` | Dates, follow-up rules, site targets, and programme periods | Change denominators, expected submissions, or recruitment target displays |
| `monitoring` | Operational alert thresholds | Decide when someone appears on a reminder or follow-up list |
| `protocol_monitoring` | Cross-form screening rules and provisional classifications | Enable, disable, or classify potential protocol deviations and violations |
| `demographics` | Age and initiation-time groupings | Change category boundaries and labels on page 2 |
| `site_breakdowns` | Site-specific chart switches | Show or suppress selected site comparisons |
| `bodymap` | Pain-map titles and region limits | Display all regions or restrict long supporting results |
| `cycle_inference` | Rules used to infer menstrual onset and cycles | Decide whether spotting can start a cycle and set plausible onset intervals |
| `display` | Programme, inferred-cycle, and cycle-day windows | Control how much follow-up appears in charts |
| `uncertainty` | Confidence interval settings | Change the confidence level or number of participant bootstrap samples |
| `labels` | Human-readable names | Replace site codes with names shown to readers |
| `dummy_data` | Development-data size and simulation settings | Create a larger or different test dataset without affecting production data |

### Switching between dummy and production data

The controlling setting is:

```yaml
data_source:
  mode: development
```

Use `development` while testing with the dummy datasets. For live Kobo data, enter the correct server and asset UIDs under `data_source.production`, store the API token in the environment variable named by `api_token_environment_variable`, and then change the mode to `production`.

The API token itself must **not** be written into `dashboard_config.yml` or committed to GitHub. Production action lists are also excluded from the rendered site by default because they can contain participant identifiers or contact information.

During early live testing, Kobo may omit a question from its JSON response when every downloaded submission skipped that question. The importer therefore treats unanswered monthly outcome fields as empty rather than assuming the connected asset is wrong. When a test record lacks the form's calculated report date, it uses the calendar day before the Kobo submission timestamp because CIMC questions describe “yesterday.” If no monthly records are yet due, the monthly page displays a “not yet available” explanation and will populate after the first eligible monthly submission. Participant identifiers and the core CIMC routing fields are still validated so an incorrect asset UID or incompatible form does not pass silently.

### Settings that change the meaning of results

Some settings affect presentation only, while others change the underlying calculation. Changes to the following should be agreed and documented before results are compared over time:

- `study.data_cutoff`, follow-up duration, and monthly due-day rules;
- participant ID, report-date, programme-start, or pain-location field mappings;
- any setting under `cycle_inference`;
- monitoring thresholds used to construct operational lists;
- demographic boundaries or site definitions;
- the confidence level and participant-bootstrap settings.

By contrast, chart titles, the number of intersections displayed, and the visible chart window generally change presentation rather than the source records. A shorter display window can still hide later observations from view, so it should be described clearly.

### Rebuilding the dashboard

After saving the configuration, render the complete Quarto project from the project folder. The pre-render step prepares either the dummy or Kobo data, the R code recalculates every page, and the completed HTML book is written to `docs/`.

```bash
quarto render
```

Do not manually edit files inside `docs/`: they are generated outputs and will be replaced during the next render. If a render stops after a configuration change, first check spelling, indentation, quote pairing, and whether list labels and boundaries contain compatible numbers of entries.

### What the dashboard is written in

All data preparation, statistical summaries, confidence intervals, tables, and plots are implemented in **R**. The report pages are **Quarto** documents (`.qmd`), while `dashboard_config.yml` supplies YAML settings. The published HTML also uses CSS for appearance and a small amount of JavaScript for interactive elements such as body-map hover labels. No Python analysis pipeline is used.

## Technical appendix: detailed ever-reported pain location map

This version retains every original SVG region, including left/right and dorsal/ventral distinctions. Locations come only from pain-positive daily submissions; percentages use all unique participants as the denominator, and each participant contributes at most once per detailed region across the observation period.

**What it answers.** “Did this participant ever report pain in this exact anatomical region during follow-up?” Repeated reports in the same region do not increase that participant's contribution.

**Why it is in the appendix.** The detailed map preserves laterality and body surface for clinical or instrument-development review, while the symmetric map earlier in the report provides the clearer primary summary.

```{r}
#| label: detailed-body-map
#| results: asis

detailed_map_html <- tags$div(
  id = "bodymap-report-detailed",
  class = "bodymap-report",
  tags$div(
    class = "bodymap-frame",
    HTML(detailed_bodymap$markup),
    tags$div(
      class = "tooltip bodymap-hover",
      role = "status",
      `aria-live` = "polite",
      tags$div(class = "tooltip-inner")
    )
  ),
  tags$div(
    class = "bodymap-legend",
    `aria-label` = "Colour scale: percent of all participants",
    tags$div(class = "bodymap-gradient"),
    tags$div(
      class = "bodymap-legend-labels",
      tags$span("0%"),
      tags$span("Percent of all participants"),
      tags$span(sprintf("%.1f%%", detailed_bodymap$maximum))
    )
  ),
  tags$div(
    class = "bodymap-note",
    "Hover over or focus a detailed body region to see its participant count and percentage."
  )
)

cat("```{=html}\n", as.character(detailed_map_html), "\n```\n", sep = "")

if (length(detailed_bodymap$unknown) > 0) {
  warning_html <- tags$div(
    class = "bodymap-warning",
    tags$strong("Unmatched detailed response codes: "),
    paste(detailed_bodymap$unknown, collapse = ", ")
  )
  cat("```{=html}\n", as.character(warning_html), "\n```\n", sep = "")
}
```

```{=html}
<script>
(function () {
  function initialiseDetailedMap() {
    const root = document.getElementById('bodymap-report-detailed');
    if (!root || root.dataset.bodymapInitialised === 'true') return;
    root.dataset.bodymapInitialised = 'true';
    const frame = root.querySelector('.bodymap-frame');
    const tooltip = root.querySelector('.bodymap-hover');
    const inner = tooltip.querySelector('.tooltip-inner');

    function regionFrom(target) {
      return target && target.closest ? target.closest('[data-bodymap-tooltip]') : null;
    }
    function show(region) {
      if (!region || !frame.contains(region)) return;
      inner.textContent = region.getAttribute('data-bodymap-tooltip');
      tooltip.classList.add('is-visible');
      const regionBox = region.getBoundingClientRect();
      const frameBox = frame.getBoundingClientRect();
      const tooltipBox = tooltip.getBoundingClientRect();
      let left = regionBox.left - frameBox.left + regionBox.width / 2 - tooltipBox.width / 2;
      left = Math.max(8, Math.min(left, frameBox.width - tooltipBox.width - 8));
      let top = regionBox.top - frameBox.top - tooltipBox.height - 8;
      if (top < 8) top = regionBox.bottom - frameBox.top + 8;
      tooltip.style.left = left + 'px';
      tooltip.style.top = top + 'px';
    }
    function hide() { tooltip.classList.remove('is-visible'); }

    root.addEventListener('pointerover', function (event) { show(regionFrom(event.target)); });
    root.addEventListener('pointerout', function (event) {
      const current = regionFrom(event.target);
      const next = regionFrom(event.relatedTarget);
      if (current && next !== current) hide();
    });
    root.addEventListener('focusin', function (event) { show(regionFrom(event.target)); });
    root.addEventListener('focusout', hide);
  }
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', initialiseDetailedMap, { once: true });
  } else {
    initialiseDetailedMap();
  }
})();
</script>
```
